### 2015-10-16 paper_BLM.tex
initial upload

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2014/09/25
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
%
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{natbib}
\linenumbers
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{epstopdf}
%\graphicspath{ {./images/results} }
\usepackage{color}
\usepackage{ctable}
%\usepackage{epsfig}
\usepackage{hyperref}
\usepackage{soul}
\usepackage{amssymb}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{Boundary-Layer Meteorology}

%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}% 
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

% ---------------------------------------------------------------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------------------------------------------
\begin{document}

\title{Exact analytic solution for slope flows with spatially varying eddy viscosity and diffusivity}

\titlerunning{Exact analytic solution for slope flows}        % if too long for running head

%\authorrunning{Short form of author list} % if too long for running head
\author{M.~G.~Giometto \and R.~Grandi\and J.~Fang \and M.B. Parlange}

\institute{ M.G. Giometto \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
		\email{marco.giometto@epfl.ch}
		\and
		Riccardo Grandi \at Mathematics Institute for Geometry and Applications, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
		 \and 
		 J. Fang \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
		 \and
		M.B. Parlange \at Civil Engineering, Faculty of Applied Sciences, University of British Columbia, Vancouver, BC, Canada
}

\date{Received: DD Month YEAR / Accepted: DD Month YEAR}
% The correct dates will be entered by the editor

\maketitle

% ABSTRACT
\begin{abstract}
An exact analytic solution of the steady-state Prandtl model equations is derived, valid for spatially varying eddy diffusivities (O'Briens type) and Prandtl number of unity. 
In this formulation profiles show significant variations in both phase and amplitude of minima-maxima with respect to the classic constant eddy viscosity model and the more recent, approximate, WKB solution. 
The near wall region is characterized by a relatively stronger surface inversion and velocity gradients, the low-level-jet is further displaced toward the wall, and its peak velocity strongly depends on the model parameter, suggesting a tighter coupling between dynamics and thermodynamics.
\end{abstract}

\section{Introduction}
Natural convection of turbulent stratified flows over sloping surfaces is ubiquitous in nature and engineering, and is of interest not only as a fundamental problem in itself, but also because of the important role it plays over a broad range of scales and applications. 
On a local scale, for instance, it governs local weather conditions, affecting atmospheric transport processes and dispersion of scalars such as heat and humidity \citep{Monti2002, Nylen2004b}. 
On a regional scale, it drives the development of deep-convective circulations \citep{Egger1985, Parish1998} and is responsible for intense cyclonic vorticity in the middle and upper troposphere \citep{Parish1992}.
Further, recent experimental field campaigns \citep{Chu1987, Oerlemans1993} have shown that persistent katabatic winds characterize the atmospheric boundary layer over snow-ice surfaces and glaciers, and therefore an accurate characterization of such flows is an essential component of understanding and modeling of the weather and climate.
However, the complex dynamics (e.g. occurrence of intermittency, waves, Kelvin-Helmholtz instabilities and low-level jets) and the lack of a satisfactory similarity theory for such flows \citep{Nadeau2012} pose a heavy burden in terms of computational requirements for numerical modellers; in most cases the required resolution is prohibitively costly \citep{Shapiro2004, Shapiro2004a, Fedorovich2009, Fedorovich2009d, Burkholder2011a}.
Because of this, conceptual models are still of great interest, and represent a valid tool for the characterization of such systems. 
A cornerstone in the understanding of natural convection of stratified fluid along a sloping surface is represented by the classic Prandtl analytic model \citep{Prandtl}, and its more recent extensions/generalizations to include the effects of Coriolis force \citep{Gutman1964}, external winds \citep{Lykosov_1972}, surface heterogeneity \citep{Egger1985, Shapiro2007, Oldroyd2014}.
The Prandtl model approximates the atmosphere in a Boussinesq sense and describes a steady flow over a thermally perturbed unbounded planar sloping surface that lies within a stratified environment, given by the following system of equations:
%
\begin{linenomath*}
\begin{eqnarray}
	N^2 u(z) \sin{\alpha} & = & d( K_H db/dz )/dz,
	\label{eqn1u} \\
	%
	b(z) \sin{\alpha} & = & -d( K_M du/dz )/dz,
	\label{eqn1b}
\end{eqnarray}
\end{linenomath*}
%
where $z$ denotes the normal-to-slope coordinate directions, $u$ is the downslope velocity, $b$ is buoyancy, $N$ is the buoyancy frequency characterizing the system (related to the background stratification), $\alpha$ is the slope angle and $K_M$ and $K_H$ denote the eddy viscosity and diffusivity (an eddy viscosity/diffusivity model has been used to parametrize turbulent fluxes of momentum and buoyancy).
Equations are integrated in $z \in \ [0,H]$ with boundary conditions $u(0)=0$, $u(H) = 0$, $b(0)=b_s$ and $b(H) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).

The flow is assumed to be invariant in the downslope direction and the model can be used to determine its vertical structure \citep{NAPPO1987}.
Eqs. \ref{eqn1u} and \ref{eqn1b} state that downslope (upslope) convection of cold (warm) air is balanced by momentum flux divergence, and that along-slope generated buoyancy is balanced by buoyancy flux divergence; thus the model is applicable away from ridges and valleys, so that advection terms are negligible \citep{NAPPO1987}.
The Prandtl constant-K model is known to be overdissipative in the near surface regions, and therefore not able to represent the observed strong surface gradients of temperature and momentum that commonly characterize katabatic and anabatic flows \citep{Oerlemans1998, grisogono2001katabatic}. 
Simple variations in the eddy diffusivity profiles were introduced in an exact analytic solution by \citet{gutman_1983}, and more recently \citet{grisogono2001katabatic} considered general variations in the vertical structure of the eddy diffusivities, and derived  solutions based on the WKB approximation.
The WKB solution is able to account for additional dynamics while still retaining an elegant form.
However, that theory is only applicable when the model parameters $(K_M, K_H)$ vary more slowly than the solution $(u,b)$, and the validity of such a constraint for slope flows has been the subject of great debate \citep{Grisogono2002}.
In the following, we derive a closed-form solution to the Prandtl-model equations, valid for O'Brien's type \citep{O'Brien1970} eddy diffusivities and representing an exact alternative to the WKB solution -- for the chosen form of the model parameter.

% ###################################################################
\section{The Analytic Solution}
%
We consider the one-dimensional Prandtl model equations \ref{eqn1u} and \ref{eqn1b}. Assuming $Pr=1$ (i.e. $K_M=K_H=K$) and assigning length, velocity and buoyancy scales as $L=\max{(K)}^{1/2} N^{-1/2} \sin^{-1/2}{\alpha}$, $U=b_s N^{-1}$ and $B=b_s$ Eqs. \ref{eqn1u} and \ref{eqn1b} can be reduced to:
%
\begin{linenomath*}
\begin{subequations}
\label{ode}
\begin{align}
	u^+& = d( K^+ db^+/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
	\label{eqn1u_norm} \\
	%
	b^+ & = -d( K^+ du^+/dz^+ )/dz^+, &&\mathrm{in}  \ [0,H^+]
	\label{eqn1b_norm}
\end{align}
\end{subequations}
\end{linenomath*}
%
respectively, where $K^+$ is a normalized eddy viscosity, $z^+=zL^{-1}$, $u^+ = uU^{-1}$, $b^+=b B^{-1}$, with boundary conditions $u^+(0)=0$, $u^+(H^+) = 0$, $b^+(0)=\pm 1$ and $b^+(H^+) = 0$.
%
Further, we introduce the following variables 
%
\begin{linenomath*}
\begin{equation}
   f_1= b^+ - i u^+ \hspace{3mm} \textrm{and} \hspace{3mm} f_2=b^+ + iu^+,
   \label{combinationVars}
\end{equation}
\end{linenomath*}
%
and upon substitution of Eqs. \ref{eqn1u_norm} and \ref{eqn1b_norm} into Eqs. \ref{combinationVars}, the system can be decoupled to obtain two (independent) complex ordinary differential equations (ODEs) for the canonical variables $f_1$ and $f_2$:
%
\begin{linenomath*}
\begin{subequations}
\label{ode_norm}
\begin{align}
	i \cdot f_1 &=  d(  K^+ df_1/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
	\label{ode1} \\
	i \cdot f_2 &= - d( K^+ df_2/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
	\label{ode2}
\end{align}
\end{subequations}
\end{linenomath*}
%
with boundary conditions $f_i(0)=\pm 1$ and $f_i(H^+) = 0$, $i=1,2$.

We assume eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz. $K^+ = A^+ (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$, where
$\epsilon^+$ is an additional parameter that we introduce in order to shift the zeroes of $K^+$ outside the interval of integration $[0,H^+]$.
$\epsilon^+$ can be tuned to provide the desired value of viscosity / diffusivity at the wall.

In order to solve Eqs. \ref{ode1} and \ref{ode2}, we observe that both have the form
%
\begin{linenomath*}
\begin{equation*}
	f= \mp i \cdot d/dz^+ ( K^+ df/dz^+ ),
\end{equation*}
\end{linenomath*}
%
and therefore can be solved using the same method. First, we rewrite the equation in canonical form:
%
\begin{linenomath*}
\begin{align}
	\label{can_form}
	f''+P f'+ Qf &=0, && \mathrm{in}  \ [0,H^+]
\end{align}
\end{linenomath*}
%
where $P(z^+)=(K^+)'/K^+$ and $Q(z^+)=1/(\pm i K^+)$. Second, it is an easy computation to show that, if $f$ solves Eq. \ref{can_form} then $g(z^+):=f( (H^++2 \epsilon^+) z^+- \epsilon^+)$ solves:
%
\begin{linenomath*}
\begin{align}
	\label{can_form_sec}
	g''+\widetilde{P} g'+ \widetilde{Q} g =0, && \mathrm{in}  \ [0,1]
\end{align}
\end{linenomath*}
%
where $\widetilde{P}(z^+)=\gamma'(z^+)/\gamma(z^+)$ and $\widetilde{Q}(z^+)=1/(\pm i \cdot A^+ \cdot (H^++2\epsilon^+) \gamma(z^+))$, with $\gamma(z^+)=z^+(z^+-1)^2$.
Eqn. \ref{can_form_sec} is a second order ODE with three regular singular points at $z^+ = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
This special case is known as the \emph{equation of Papperitz} and its general solution is:
%
%\begin{widetext}
\begin{linenomath*}
\begin{equation}
	g(z^+) = \alpha (1-z^+)^\mu \ _2F_1 (\mu, 1- \mu', 1+\mu-\mu', 1-z^+)
	+\beta (1-z^+)^{\mu'} \ _2F_1 (\mu', 1- \mu, 1+\mu'-\mu, 1-z^+),
	\label{gen_sol_g}
\end{equation}
\end{linenomath*}
%\end{widetext}
%
where $\ _2F_1$ are \emph{Gaussian hypergeometric functions} and $\mu$, $\mu'$ are the solutions to the degree two equation
%
\begin{linenomath*}
\begin{equation*}
	x^2+x+1/(\pm i A^+(H^++2 \epsilon^+))=0,
\end{equation*}
\end{linenomath*}
%
depending on which of Eqs. \ref{can_form_sec} we are solving.
Note that the general solution to Eq. \ref{can_form_sec} is also often written using the \emph{Riemann symbol}:
%
\begin{linenomath*}
\begin{equation*}
\left \{
\begin{array}{cccc}
0 & 1 & \infty &  \\
\lambda & \mu & \nu & z^+\\
\lambda' & \mu' & \nu' & \\
\end{array}
\right \}
\end{equation*}
\end{linenomath*}
%
where, in this case, $\mu$ and $\mu'$ are as above, $\lambda=\lambda'=0$ and $\nu=0$, $\nu'=2$.
%
To retrieve the general solution to Eq. \ref{can_form} it is sufficient to substitute $(z^++\epsilon^+)/(H^+ +2 \epsilon^+)$ in place of $z^+$ in Eq. \ref{gen_sol_g}.
As the integration constants $\alpha$ and $\beta$ are specified through the imposition of boundary conditions, back-substituting $b^+ = (f_1+f_2)/2$ and $u^+ = -(f_1-f_2)/2i$ yields the solution in terms of $u^+$ and $b^+$.

% ####################################################################
\section{Examples}
%
\begin{figure}
   \begin{center}
      \includegraphics[width= 70.0mm]{./u-b_log}
      \caption{Comparison of the new analytic solution (A1) against the constant-$K$ (A2), the WKB (A3) and a numerical $1D$ solution (N1). Analytic profiles of normalized velocity $(u^+)$ are denoted with dot-dashed lines whereas analytic profiles of normalized buoyancy $(b^+)$ are denoted by dashed lines. Here $K^+ = A^+ \cdot (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$ where $A^+=6.75 e-4$, $\epsilon^+ =1.5 \times 10^{-3}$ and $H^+ = 10$. A corresponding dimensional profile is characterized by $\max{(K)} = 0.1 \ \mathrm{m^2s^{-1}}$ and $K(z=0) = 10^{-5} \ \mathrm{m^2s^{-1}}$, in agreement with common atmospheric values.}
      \label{fig1}
   \end{center}
\end{figure}
%
\begin{figure}
    \begin{center}
    \includegraphics[width= 70.0mm]{./u-b_log_various_K}
    \caption{Sensitivity of A1 (left) and A3 (right) profiles to variations in the diffusivity coefficient $K^+$. Normalized velocity values $(u^+)$ are denoted with dot-dashed lines whereas normalized buoyancy values $(b^+)$ with dashed lines. Equations are integrated in  the interval $z^+ \in [0,10]$, which is fully shown in the plot. Here we considered $A^+=6.75 \times 10^{-4}$ and $\epsilon^+  = (7.4,1.5,0.30,0.06) \times 10^{-3}$. Under the constraint $K(z=0) = 10^{-5} \ \mathrm{m^2s^{-1}}$, the corresponding set of dimensional kynematic diffusivities satisfy $\max{(K)}=0.002,0.01,0.05,0.25 \ \mathrm{m^2s^{-1}}$.}
    \label{fig3}
    \end{center}
\end{figure}
%
In Fig. \ref{fig1} we compare the new analytic solution (A1 in the following) against the constant-$K$ (A2), the WKB (A3) and a numerical solution (N1).
The constant-$K$ value is fixed to $K^+_{\mathrm{A2}} = \max(K_{\mathrm{A1}}^+)/3$. 
Profiles for N1 are derived by solving monolithically the system of ODEs defined by Eqs. \ref{eqn1u_norm} and \ref{eqn1b_norm}, adopting a second-order accurate centered finite difference discretization with over $40,000$ collocation points and stretching the grid via a quadratic coordinate transform (at such resolution profiles are invariant to further refinements down to machine precision).
The excellent match between A1 and N1 certifies the quality of results for both methods. 
In comparison to its analytical counterparts, A1 shows a remarkably strong inversion in the near surface regions $(z^+ <1)$, suggesting overdiffusive behaviour of both A2 and A3, which are incapable of providing such strong buoyancy gradients. 
For instance, normalized surface buoyancy gradients of simulation A1 are over an order of magnitude larger than those of A2 $( (db/dz)^+_\mathrm{A1}/(db/dz)^+_\mathrm{A2} = \mathcal{O}(10)$ as $z^+ \rightarrow 0$).
Despite this, we observe a relatively good match between $u^+_\mathrm{A1}$ and $u^+_\mathrm{A3}$ in the interval $z^+ \in [0,1]$, which confirms the enhanced dissipative properties of the A3 solution, when compared against the constant-$K$ approach. 
To understand the importance of a decreasing eddy viscosity in the near surface regions, it is worth noting that $(du/dz)^+_\mathrm{A1}/(du/dz)^+_\mathrm{A2} = \mathcal{O}(10)$, whereas $(du/dz)^+_\mathrm{A1}/(du/dz)^+_\mathrm{A3}= \mathcal{O}(1)$ as $z^+ \rightarrow 0$.
Overall the new solution exhibits significant variations when compared against A2 and A3, in both amplitude and location of maxima-minima. 
For instance, both the low-level jet height and the peak normalized velocity are significantly reduced, features that are of great importance for an accurate representation of the stable boundary layer and from a parameterization perspective \citep{Mahrt1998}.
Further, from Fig. \ref{fig3}, it is clear that $\max{(u^+_\mathrm{A1})}$ now depends on the diffusive properties of the flow, i.e. $\max{(u^+_{\mathrm{A1}})} = f(K^+)$, in constrast to its analytic counterparts, which predict $\max{(u^+_\mathrm{A2})} = \max{(u^+_\mathrm{A3})} =  \sqrt{2}/2 [(e^{(\pi/4)})/\sqrt{Pr}] = 0.32$, regardless of $K^+$.
$u^+_{\mathrm{A1}}$ and $b^+_{\mathrm{A1}}$ also show a stronger dependence on the $K+$ parameter with respect to A3 profiles, in particular in the $z^+ \in [0,1]$ interval.
Overall, A1 predicts significantly reduced mass and buoyancy (horizontal) fluxes, viz. $\int_0^{H^+}{u^+}{dz^+},\int_0^{H^+}{b^+}{dz^+}$, with respect to A3.
%
% new part
%
\begin{figure}
    \begin{center}
    \includegraphics[width= 70.0mm]{./u_dim_alpha_N_b}
    \caption{Family of dimensional velocity profiles derived from re-dimensionalization of a reference normalized solution. The normalized solution is obtained in $z^+ \in [0,10]$ for $A^+ = 6.75 \times 10^{-4}$ and $\epsilon^+ =1.5 \times 10^{-3}$ (assuming $K(z=0) = 10^{-5}  \ \mathrm{m^2s^{-1}}$, the corresponding dimensional kynematic diffusivities satisfy $\max{(K)}=0.01 \ \mathrm{m^2s^{-1}}$). The considered set of parameters are reported in Table \ref{table}. Decreasing values of the parameters (with respect to the reference ones) are denoted with solid lines, increasing values by dashed lines.}
    \label{fig2}
    \end{center}
\end{figure}
%
\begin{table}
\caption{Set of parameters for re-normalization of the reference solution. The reference normalized solution is computed adopting $H^+ = 10, A^+ = 6.75 \times 10^{-4}, \epsilon^+ =1.5 \times 10^{-3}$.}
\label{table}
\centering
\begin{tabular}{l l l l l l l l}
\hline
 Value & Ref. & $\alpha1$ & $\alpha_2$ & $N_1$ & $N_2$ & $b_{s,1}$ & $b_{s,2}$ \\
\hline
   $\alpha \ (\mathrm{deg})$ & 30 & 15 & 60 & 30 & 30 & 30 & 30  \\
   $N \ (\mathrm{Hz})$ & 0.01 & 0.01 & 0.01 & 0.005 & 0.02 & 0.01 & 0.01 \\
   $b_s \ (\mathrm{ms^{-2}})$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 & 0.15 & 0.60 \\
\hline
\end{tabular}
\end{table}
%
To get acquainted with the proposed normalization Fig. \ref{fig2} proposes a set of re-dimensionalized velocity profiles $u \ \mathrm{(ms^{-1})}$ from a reference normalized solution.
We propose a reference dimensional solution, characterized by $\alpha = 30 \ \mathrm{deg}, N = 0.01 \ \mathrm{Hz}$ and $b_s = 0.3  \ \mathrm{ms^{-2}}$, and consider variations in both sloping angle $\alpha$, imposed buoyancy frequency $N$ and imposed surface buoyancy $b_s$ (see Table \ref{table}).
Variations in the sloping angle $\alpha$ result in a modification of the normalization constant $L \propto \sin^{-1/2}$ which acts as a stretching of the independent variable $z$ (no effects on $\max{(u)}$). 
In particular, the steeper the angle, the smaller the characteristic scales of the flow will become.
Variations in the background stratification, viz. $N$, will modify both $L \propto N^{-1/2}$ and $U \propto N^{-1}$, yielding changes in the system, whose lengths and velocities will tend to decrease (increase) with increasing (decreasing) $N$.
Further, variations in the prescribed surface buoyancy $b_s$ will scale both buoyancy and velocity profiles accordingly, since $b(z) \propto b_s$ and $u(z) \propto b_s$.
As in both the classic Prandtl and WKB linear models, $K^+$ needs to be assigned a-priori; it is not coupled and does not feed back into the solution, which represents the main weakness of such linear approaches \citep{grisogono2001katabatic}.

% ####################################################################
\section{Conclusions}
%
We have derived a closed-form analytic solution of the Prandtl model equations, based on an ad hoc decoupling of the system and specific choice of the model parameter, resulting in a set of \textit{equations of Papperitz}, characterized by three regular singular points. 
The new solution is valid for O'Brien-type eddy diffusivities (cubic polynomials) and Prandtl number of unity. 
For the considered settings the new solution represents an improvement with respect to both the classic constant-$K$ and the more recent WKB solutions. 
New profiles show significant variations in both phase and amplitude of minima-maxima, stronger surface gradients are combined with overall reduced horizontal fluxes and the LLJ is further displaced toward the wall.
The new solution suggests a somewhat different coupling between velocity and buoyancy -- when compared against its analytical counterparts, showing a diffusivity dependent peak velocity and a remarkably strong inversion layer in the near surface location.
In addition to a theoretical insight, the proposed solution can be used to improve future stable boundary layer parameterizations when coupled with other parts of the boundary layer physics.

% ####################################################################
\section{Acknowledgements}
%
This research was primarily funded by the Swiss National Science Foundation (SNSF-200021-134892) and by the Competence Center for Environmental Sustainability (CCES-SwissEx) of the ETH domain. We are also grateful for funding from the NSERC Discovery Grant program.

%\appendix?

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{/Users/mg/Phd/papers/bib_files/library}

\begin{thebibliography}{26}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem[{Chu(1987)}]{Chu1987}
Chu PC (1987) {An instability theory of ice-air interaction for the formation
  of ice edge bands}. Journal of Geophysical Research 92(7):6966,
  \doi{10.1029/JC092iC07p06966}

\bibitem[{Egger(1985)}]{Egger1985}
Egger J (1985) {Slope Winds and the Axisymmetric Circulation over Antarctica}.
  Journal of the Atmospheric Sciences 42:1859--1867,
  \doi{10.1175/1520-0469(1985)042<1859:SWATAC>2.0.CO;2}

\bibitem[{Fedorovich and Shapiro(2009{\natexlab{a}})}]{Fedorovich2009d}
Fedorovich E, Shapiro A (2009{\natexlab{a}}) {Structure of numerically
  simulated katabatic and anabatic flows along steep slopes}. Acta Geophysica
  57(4):981--1010, \doi{10.2478/s11600-009-0027-4},
  \urlprefix\url{http://www.springerlink.com/index/10.2478/s11600-009-0027-4}

\bibitem[{Fedorovich and Shapiro(2009{\natexlab{b}})}]{Fedorovich2009}
Fedorovich E, Shapiro A (2009{\natexlab{b}}) {Turbulent natural convection
  along a vertical plate immersed in a stably stratified fluid}. Journal of
  Fluid Mechanics 636:41, \doi{10.1017/S0022112009007757}

\bibitem[{Grisogono and Oerlemans(2001)}]{grisogono2001katabatic}
Grisogono B, Oerlemans J (2001) {Katabatic Flow: Analytic Solution for
  Gradually Varying Eddy Diffusivities}. Journal of the Atmospheric Sciences
  58(21):3349--3354,
  \doi{http://dx.doi.org/10.1175/1520-0469(2001)058<3349:KFASFG>2.0.CO;2}

\bibitem[{Grisogono and Oerlemans(2002)}]{Grisogono2002}
Grisogono B, Oerlemans J (2002) {Justifying the WKB approximation in pure
  katabatic flows}. Tellus, A 54(5):453--462,
  \doi{10.1034/j.1600-0870.2002.201399.x}

\bibitem[{Gutman(1983)}]{gutman_1983}
Gutman LN (1983) {On the theory of the katabatic slope wind}. Tellus, A
  35(3):332--335, \doi{10.3402/tellusa.v35i3.11434}

\bibitem[{Gutman and Malbakhov(1964)}]{Gutman1964}
Gutman LN, Malbakhov VM (1964) {On the Theory of the Katabatic Winds of
  Antarctica}. University of Melbourne, Meteorology Department

\bibitem[{Lykosov and Gutman(1972)}]{Lykosov_1972}
Lykosov VN, Gutman LN (1972) {Turbulent boundary layer above a sloping
  inderlying surface}. Proceedings of the USSR Academy of Sciences 8:799--809,
  \urlprefix\url{papers2://publication/uuid/B2EC0692-4251-4224-8185-A1AE8D9B00E9}

\bibitem[{Mahrt(1998)}]{Mahrt1998}
Mahrt L (1998) {Stratified Atmospheric Boundary Layers and Breakdown of
  Models}. In: Theoretical and Computational Fluid Dynamics, vol~11, pp
  263--279, \doi{10.1007/s001620050093},
  \urlprefix\url{http://link.springer.com/10.1007/s001620050093}

\bibitem[{Monti et~al.(2002)Monti, Fernando, Princevac, Chan, Kowalewski, and
  Pardyjak}]{Monti2002}
Monti P, Fernando HJS, Princevac M, Chan WC, Kowalewski TA, Pardyjak ER (2002)
  {Observations of Flow and Turbulence in the Nocturnal Boundary Layer over a
  Slope}. Journal of the Atmospheric Sciences 59:2513--2534,
  \doi{10.1175/1520-0469(2002)059<2513:OOFATI>2.0.CO;2}

\bibitem[{Morse and Feshbach(1953)}]{Morse1954a}
Morse PM, Feshbach H (1953) {Methods of Theoretical Physics}. McGraw-Hill

\bibitem[{Nadeau et~al.(2013)Nadeau, Pardyjak, Higgins, and
  Parlange}]{Nadeau2012}
Nadeau DF, Pardyjak ER, Higgins CW, Parlange MB (2013) {Similarity Scaling Over
  a Steep Alpine Slope}. Boundary-Layer Meteorology 147(3):401--419,
  \doi{10.1007/s10546-012-9787-5},
  \urlprefix\url{http://link.springer.com/10.1007/s10546-012-9787-5}

\bibitem[{Nappo and Shankar(1987)}]{NAPPO1987}
Nappo CJ, Shankar RK (1987) {A model study of pure katabatic flows}. Tellus A
  39(1):61--71, \doi{10.3402/tellusa.v39i1.11740},
  \urlprefix\url{http://onlinelibrary.wiley.com/doi/10.1111/j.1600-0870.1987.tb00289.x/abstract}

\bibitem[{Nylen et~al.(2004)Nylen, {Andrew G. F.}, and Doran}]{Nylen2004b}
Nylen TH, {Andrew G F}, Doran PT (2004) {Climatology of katabatic winds in the
  McMurdo dry valleys, southern Victoria Land, Antarctica}. Journal of
  Geophysical Research 109:1--9, \doi{10.1029/2003JD003937}

\bibitem[{O'Brien(1970)}]{O'Brien1970}
O'Brien JJ (1970) {A Note on the Vertical Structure of the Eddy Exchange
  Coefficient in the Planetary Boundary Layer}. Journal of the Atmospheric
  Sciences 27:1213--1215,
  \doi{10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2},
  \urlprefix\url{http://dx.doi.org/10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2}

\bibitem[{Oerlemans(1998)}]{Oerlemans1998}
Oerlemans J (1998) {The atmospheric boundary layer over melting glaciers}. In:
  Clear and Cloudy Boundary Layers, vol~48, Royal Netherlands Academy of Arts
  and Sciences, pp 129--153,
  \urlprefix\url{http://igitur-archive.library.uu.nl/phys/2007-0716-203217/oerlemans\_07\_atmosphericboundarylayer.pdf}

\bibitem[{Oerlemans and Vugts(1993)}]{Oerlemans1993}
Oerlemans J, Vugts HF (1993) {A Meteorological Experiment in the Melting Zone
  of the Greenland Ice Sheet}. Bulletin of the American Meteorological Society
  74(3):355--365, \doi{10.1175/1520-0477(1993)074<0355:AMEITM>2.0.CO;2}

\bibitem[{Oldroyd et~al.(2014)Oldroyd, Katul, Pardyjak, and
  Parlange}]{Oldroyd2014}
Oldroyd HJ, Katul G, Pardyjak ER, Parlange MB (2014) {Momentum balance of
  katabatic flow on steep slopes covered with short vegetation}. Geophysical
  Research Letters 41:4761--4768, \doi{10.1002/2014GL060313}

\bibitem[{Parish(1992)}]{Parish1992}
Parish TR (1992) {On the Role of Antarctic Katabatic Winds in Forcing
  Large-Scale Tropospheric Motions}. Journal of the Atmospheric Sciences
  49:1374--1385, \doi{10.1175/1520-0469(1992)049<1374:OTROAK>2.0.CO;2}

\bibitem[{Parish and Bromwich(1998)}]{Parish1998}
Parish TR, Bromwich DH (1998) {A Case Study of Antarctic Katabatic Wind
  Interaction with Large-Scale Forcing}. Monthly Weather Review 126:199--209,
  \doi{10.1175/1520-0493(1998)126<0199:ACSOAK>2.0.CO;2}

\bibitem[{Prandtl(1942)}]{Prandtl}
Prandtl L (1942) {F\"{u}hrer durch die Str\"{o}mungslehre}. Vieweg \& Sohn,
  Braunschweig

\bibitem[{Shapiro and Fedorovich(2004{\natexlab{a}})}]{Shapiro2004a}
Shapiro A, Fedorovich E (2004{\natexlab{a}}) {Prandtl number dependence of
  unsteady natural convection along a vertical plate in a stably stratified
  fluid}. International Journal of Heat and Mass Transfer 47(22):4911--4927,
  \doi{10.1016/j.ijheatmasstransfer.2004.04.035},
  \urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0017931004002157}

\bibitem[{Shapiro and Fedorovich(2004{\natexlab{b}})}]{Shapiro2004}
Shapiro A, Fedorovich E (2004{\natexlab{b}}) {Unsteady convectively driven flow
  along a vertical plate immersed in a stably stratified fluid}. Journal of
  Fluid Mechanics 498:333--352, \doi{10.1017/S0022112003006803},
  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112003006803}

\bibitem[{Shapiro and Fedorovich(2007)}]{Shapiro2007}
Shapiro A, Fedorovich E (2007) {Katabatic flow along a differentially cooled
  sloping surface}. Journal of Fluid Mechanics 571:149,
  \doi{10.1017/S0022112006003302},
  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112006003302}

\bibitem[{Spalart et~al.(2011)Spalart, Strelets, and
  Garbaruk}]{Burkholder2011a}
Spalart P, Strelets M, Garbaruk A (2011) {Quality and Reliability of Large-Eddy
  Simulations II}. In: Evaluating Subgrid-ScaleModels for Large-Eddy Simulation
  of Turbulent Katabatic Flow, vol~16, pp 253--267,
  \doi{10.1007/978-94-007-0231-8},
  \urlprefix\url{http://www.springerlink.com/index/10.1007/978-94-007-0231-8}

\end{thebibliography}

\end{document}

### 2015-10-25 paper_BLM.tex
old solution

@@
 The near wall region is characterized by a relatively stronger surface inversion and velocity gradients, the low-level-jet is further displaced toward the wall, and its peak velocity strongly depends on the model parameter, suggesting a tighter coupling between dynamics and thermodynamics.
+%The new solution is used to define vertical resolution requirements in numerical studies based on the Prandtl model, which is of practical interest.
 \end{abstract}
@@
 However, the complex dynamics (e.g.
-occurrence of intermittency, waves, Kelvin-Helmholtz instabilities and low-level jets) and the lack of a satisfactory similarity theory for such flows \citep{Nadeau2012} pose a heavy burden in terms of computational requirements for numerical modellers; in most cases the required resolution is prohibitively costly \citep{Shapiro2004, Shapiro2004a, Fedorovich2009, Fedorovich2009d, Burkholder2011a}.
+occurrence of intermittency, waves, Kelvin-Helmholtz instabilities and low-level jets) and the lack of a satisfactory similarity theory for such flows \citep{Nadeau2012} pose a heavy burden in terms of computational requirements for numerical modellers; in most cases the required resolution is prohibitively costly \citep{Fedorovich2009, Fedorovich2009d, Burkholder2011a}.
 Because of this, conceptual models are still of great interest, and represent a valid tool for the characterization of such systems. 
-A cornerstone in the understanding of natural convection of stratified fluid along a sloping surface is represented by the classic Prandtl analytic model \citep{Prandtl}, and its more recent extensions/generalizations to include the effects of Coriolis force \citep{Gutman1964}, external winds \citep{Lykosov_1972}, surface heterogeneity \citep{Egger1985, Shapiro2007, Oldroyd2014}.
+A cornerstone in the understanding of natural convection of stratified fluid along a sloping surface is represented by the classic Prandtl analytic model \citep{Prandtl}, and its more recent extensions/generalizations to include the effects of Coriolis force \citep{Gutman1964}, external winds \citep{Lykosov_1972}, surface heterogeneity \citep{Shapiro2007, Oldroyd2014}.
 The Prandtl model approximates the atmosphere in a Boussinesq sense and describes a steady flow over a thermally perturbed unbounded planar sloping surface that lies within a stratified environment, given by the following system of equations:
@@
 where $z$ denotes the normal-to-slope coordinate directions, $u$ is the downslope velocity, $b$ is buoyancy, $N$ is the buoyancy frequency characterizing the system (related to the background stratification), $\alpha$ is the slope angle and $K_M$ and $K_H$ denote the eddy viscosity and diffusivity (an eddy viscosity/diffusivity model has been used to parametrize turbulent fluxes of momentum and buoyancy).
-Equations are integrated in $z \in \ [0,H]$ with boundary conditions $u(0)=0$, $u(H) = 0$, $b(0)=b_s$ and $b(H) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).
+Equations are defined in $z \in \ [0,\infty)$ with boundary conditions $u(0)=0$, $u(z \rightarrow \infty) = 0$, $b(0)=b_s$ and $b(z \rightarrow \infty) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).
 
-The flow is assumed to be invariant in the downslope direction and the model can be used to determine its vertical structure \citep{NAPPO1987}.
+The flow is assumed to be invariant in the downslope direction and the model can be used to determine its vertical structure.
 Eqs.
@@
 The Prandtl constant-K model is known to be overdissipative in the near surface regions, and therefore not able to represent the observed strong surface gradients of temperature and momentum that commonly characterize katabatic and anabatic flows \citep{Oerlemans1998, grisogono2001katabatic}.
-Simple variations in the eddy diffusivity profiles were introduced in an exact analytic solution by \citet{gutman_1983}, and more recently \citet{grisogono2001katabatic} considered general variations in the vertical structure of the eddy diffusivities, and derived  solutions based on the WKB approximation.
+Simple variations in the eddy diffusivity profiles were introduced in a matched analytic solution by \citet{gutman_1983}, and more recently \citet{grisogono2001katabatic} considered general variations in the vertical structure of the eddy diffusivities, and derived  solutions based on the WKB approximation \citep{Bender1999}.
 The WKB solution is able to account for additional dynamics while still retaining an elegant form.
 However, that theory is only applicable when the model parameters $(K_M, K_H)$ vary more slowly than the solution $(u,b)$, and the validity of such a constraint for slope flows has been the subject of great debate \citep{Grisogono2002}.
-In the following, we derive a closed-form solution to the Prandtl-model equations, valid for O'Brien's type \citep{O'Brien1970} eddy diffusivities and representing an exact alternative to the WKB solution -- for the chosen form of the model parameter.
+In the following, we derive a closed-form solution to the Prandtl-model equations, valid for eddy viscosity / diffusivity coefficients that are modelled as a limited range of cubic polynomials, similar to what proposed in \citet{O'Brien1970} for the planetary boundary layer.
+The solution thus represents an exact alternative to the WKB formulation for the chosen form of the model parameter.
+The new solution, expressed as a combination of Gaussian hypergeometric functions, is found to significantly differ from its analytical counterparts, shedding new light on the problem, and suggesting a different coupling between the dynamic and the thermodynamic boundary layers.
 
@@
 %
-We consider the one-dimensional Prandtl model equations \ref{eqn1u} and \ref{eqn1b}.
-Assuming $Pr=1$ (i.e.
-$K_M=K_H=K$) and assigning length, velocity and buoyancy scales as $L=\max{(K)}^{1/2} N^{-1/2} \sin^{-1/2}{\alpha}$, $U=b_s N^{-1}$ and $B=b_s$ Eqs.
-\ref{eqn1u} and \ref{eqn1b} can be reduced to:
+We consider the one-dimensional Prandtl model (Eq. \ref{eqn1u} and \ref{eqn1b}).
+
+Assuming eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz.
+$K(z) = A (z + \epsilon)(z-\zeta)^2$, where $\epsilon>0$ and $\zeta>H$ are parameters that we introduce in order to shift the zeroes of $K$ outside the interval of integration $[0,H]$, assuming $Pr=1$ (i.e.
+$K_M=K_H=K$) and assigning a length, velocity and buoyancy scale $L= (N \sin{\alpha})/ A$, $U=b_s N^{-1}$ and $B=b_s$ respectively, Eqs.
+\ref{eqn1u} and \ref{eqn1b} reduce to:
 %
@@
 \begin{align}
-	u^+& = d( K^+ db^+/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
+	\overline{u} & = d( \overline{K} d\overline{b}/d\overline{z} )/d\overline{z}, && \mathrm{in}  \ [0,\overline{H}]
 	\label{eqn1u_norm} \\
 	%
-	b^+ & = -d( K^+ du^+/dz^+ )/dz^+, &&\mathrm{in}  \ [0,H^+]
+	\overline{b} & = -d( \overline{K} d\overline{u}/d\overline{z} )/d\overline{z}, &&\mathrm{in}  \ [0,\overline{H}]
 	\label{eqn1b_norm}
@@
 %
-respectively, where $K^+$ is a normalized eddy viscosity, $z^+=zL^{-1}$, $u^+ = uU^{-1}$, $b^+=b B^{-1}$, with boundary conditions $u^+(0)=0$, $u^+(H^+) = 0$, $b^+(0)=\pm 1$ and $b^+(H^+) = 0$.
+where $\overline{K} = (\overline{z} + \overline{\epsilon})(\overline{z}-\overline{\zeta})^2$ is the normalized eddy viscosity/diffusivity, $\overline{z}=zL^{-1}$, $\overline{u} = uU^{-1}$, $\overline{b}=b B^{-1}$, with boundary conditions $\overline{u}(0)=0$, $\overline{u}(\overline{H}) = 0$, $\overline{b}(0)=\pm 1$ and $\overline{b}(\overline{H}) = 0$.
+Overbars $\overline{(\cdot)}$ will be omitted hereafter.
 %
-Further, we introduce the following variables 
+Further, we introduce the following variable
 %
@@
 \begin{equation}
-   f_1= b^+ - i u^+ \hspace{3mm} \textrm{and} \hspace{3mm} f_2=b^+ + iu^+,
-   \label{combinationVars}
+   f= b + i u,
+   \label{combinationVar}
 \end{equation}
@@
 and upon substitution of Eqs.
-\ref{eqn1u_norm} and \ref{eqn1b_norm} into Eqs.
-\ref{combinationVars}, the system can be decoupled to obtain two (independent) complex ordinary differential equations (ODEs) for the canonical variables $f_1$ and $f_2$:
+\ref{eqn1u_norm} and \ref{eqn1b_norm} into Eq.
+\ref{combinationVar}, the system results into a complex ordinary differential equation (ODE) for the canonical variable $f$:
 %
 \begin{linenomath*}
-\begin{subequations}
 \label{ode_norm}
-\begin{align}
-	i \cdot f_1 &=  d(  K^+ df_1/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
-	\label{ode1} \\
-	i \cdot f_2 &= - d( K^+ df_2/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
-	\label{ode2}
-\end{align}
-\end{subequations}
+\begin{equation}
+	i \cdot f =  d(  K df/dz )/dz \hspace{1cm} \mathrm{in}  \ [0,H],
+	\label{ode}
+\end{equation}
 \end{linenomath*}
 %
-with boundary conditions $f_i(0)=\pm 1$ and $f_i(H^+) = 0$, $i=1,2$.
-
-We assume eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz. $K^+ = A^+ (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$, where
-$\epsilon^+$ is an additional parameter that we introduce in order to shift the zeroes of $K^+$ outside the interval of integration $[0,H^+]$.
-$\epsilon^+$ can be tuned to provide the desired value of viscosity / diffusivity at the wall.
-
-In order to solve Eqs. \ref{ode1} and \ref{ode2}, we observe that both have the form
+with boundary conditions $f(0)=\pm 1$ and $f(H) = 0$.
+This technique for the decoupling of the system of Eqs. \ref{eqn1u_norm} and \ref{eqn1b_norm} is based on an ad hoc diagonalization.
+%
+To solve Eq. \ref{ode} we first rewrite the equation in canonical form:
 %
 \begin{linenomath*}
-\begin{equation*}
-	f= \mp i \cdot d/dz^+ ( K^+ df/dz^+ ),
-\end{equation*}
+\begin{equation}
+	\label{can_form}
+	f''+P f'+ Qf =0,
+\end{equation}
 \end{linenomath*}
 %
-and therefore can be solved using the same method. First, we rewrite the equation in canonical form:
+where $(\cdot)' = \frac{\partial (\cdot)}{\partial z}$, $P(z)=(K)'/K$ and $Q(z)=1/(i K)$.
+Second, it is an easy computation to show that rewriting Eq.
+\ref{can_form} for $y = \frac{z + \epsilon}{H + \epsilon + \zeta}
+$ results in
+%if $f$ solves Eq. \ref{can_form} then $g(z^+):=f( (H^++2 \epsilon^+) z^+- \epsilon^+)$ solves:
 %
 \begin{linenomath*}
-\begin{align}
-	\label{can_form}
-	f''+P f'+ Qf &=0, && \mathrm{in}  \ [0,H^+]
-\end{align}
+\begin{equation}
+	\label{can_form_sec}
+	f''+\widetilde{P} f'+ \widetilde{Q} f =0,
+\end{equation}
 \end{linenomath*}
 %
-where $P(z^+)=(K^+)'/K^+$ and $Q(z^+)=1/(\pm i K^+)$. Second, it is an easy computation to show that, if $f$ solves Eq. \ref{can_form} then $g(z^+):=f( (H^++2 \epsilon^+) z^+- \epsilon^+)$ solves:
-%
-\begin{linenomath*}
-\begin{align}
-	\label{can_form_sec}
-	g''+\widetilde{P} g'+ \widetilde{Q} g =0, && \mathrm{in}  \ [0,1]
-\end{align}
-\end{linenomath*}
-%
-where $\widetilde{P}(z^+)=\gamma'(z^+)/\gamma(z^+)$ and $\widetilde{Q}(z^+)=1/(\pm i \cdot A^+ \cdot (H^++2\epsilon^+) \gamma(z^+))$, with $\gamma(z^+)=z^+(z^+-1)^2$.
-Eqn. \ref{can_form_sec} is a second order ODE with three regular singular points at $z^+ = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
+where $(\cdot)' = \frac{\partial (\cdot)}{\partial y}$, $\widetilde{P}(y)=\gamma'(y)/\gamma(y)$ and $\widetilde{Q}(y)=1/( i \cdot (H+\epsilon+\zeta) \gamma(y))$, with $\gamma(y)=y(y-1)^2$.
+Eq. \ref{can_form_sec} is a second order ODE with three regular singular points at $y = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
 This special case is known as the \emph{equation of Papperitz} and its general solution is:
@@
 \begin{equation}
-	g(z^+) = \alpha (1-z^+)^\mu \ _2F_1 (\mu, 1- \mu', 1+\mu-\mu', 1-z^+)
-	+\beta (1-z^+)^{\mu'} \ _2F_1 (\mu', 1- \mu, 1+\mu'-\mu, 1-z^+),
+	f(y) = \alpha (1-y)^\mu \ _2F_1 (\mu, 1- \mu', 1+\mu-\mu', 1-y)
+	+\beta (1-y)^{\mu'} \ _2F_1 (\mu', 1- \mu, 1+\mu'-\mu, 1-y),
 	\label{gen_sol_g}
@@
 \begin{equation*}
-	x^2+x+1/(\pm i A^+(H^++2 \epsilon^+))=0,
+	x^2+x+1/( i (H+ \epsilon + \zeta))=0.
 \end{equation*}
@@
 %
-depending on which of Eqs. \ref{can_form_sec} we are solving.
 Note that the general solution to Eq. \ref{can_form_sec} is also often written using the \emph{Riemann symbol}:
@@
 0 & 1 & \infty &  \\
-\lambda & \mu & \nu & z^+\\
+\lambda & \mu & \nu & y\\
 \lambda' & \mu' & \nu' & \\
@@
 %
-To retrieve the general solution to Eq. \ref{can_form} it is sufficient to substitute $(z^++\epsilon^+)/(H^+ +2 \epsilon^+)$ in place of $z^+$ in Eq. \ref{gen_sol_g}.
-As the integration constants $\alpha$ and $\beta$ are specified through the imposition of boundary conditions, back-substituting $b^+ = (f_1+f_2)/2$ and $u^+ = -(f_1-f_2)/2i$ yields the solution in terms of $u^+$ and $b^+$.
+Upon back-substitution of the independent variable and specification of the integration constants $\alpha$ and $\beta$ (through the imposition of boundary conditions), the solution in terms of $u$ and $b$ is derived by separating the real and imaginary part of $f$
+%
+\begin{equation}
+	u(z) = \operatorname{Re}(f(z)), \hspace{1cm} b(z) = \operatorname{Im}(f(z)).
+\end{equation}
 
 % ####################################################################
+\section{Specification of of K(z)}
+
+The model assumes $Pr = 1$, i.e. $K_M = K_H = K$, although in reality they are slightly different. This assumption is justified based on the degree of accuracy of the considered study. 
+Further, as stated in the preceeding section, we assume eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz.
+$K = A(z + \epsilon)(z-\zeta)^2$, where $\epsilon>0$ can be tuned to provide the desired value of eddy viscosity / diffusivity at the wall, whereas $\zeta > H$ controls both shape and magnitude of $K$.
+The O'Brien model has often been used in studies of stable boundary layers, see for instance \citet{pielke1984mesoscale} and \citet{Stull1988}, and a generalized O'Brien model was also recently adopted in \citet{grisogono2001katabatic} to study slope flows.
+The properties of $K(z)$ in slope flows were thorougly justified in \citet{Grisogono2002};  we here recall the main criteria that $K(z)$ should honor:
+%
+\begin{enumerate}
+\item realizability condition: $K(z) \ge 0$;
+\item $K(z << \infty) = 0$;
+\item $\max(K(z))$, reached at $z=h$, must lie within the dynamic and thermal boundary layers;
+\item $h > \max(2 z_j, z_{inv})$;
+\end{enumerate}
+%
+where $z_j$ is the height of the LLJ, and $z_{inv}$ is the height of the surface inversion layer (in general we have $z_{inv} > z_j$).
+%
+In addition, assuming Monin-Obukhov similarity theory to hold for the near wall regions (which is itself a subject of great debate), one would ideally specify $K(z)$ in order to satisfy:
+%
+\begin{linenomath*}
+\begin{subequations}
+\begin{align}
+   K(z) & = \kappa u_* z/[1+\Phi(z)] & z \in [z_0,z_s], \label{MOST1}\\
+   K(z) & = f(u_*,z) \ | \ d^2f/dz^2 < 0 & z \in (z_s,H], \label{MOST2}
+\end{align}
+\end{subequations}
+\end{linenomath*}
+%
+where $z_s$ is the upper boundary of the constant-flux layer, $\Phi(z)$ is a stability correction function, $\kappa$ is the Von K\'arm\'an constant, and $u_* = \sqrt{K(du/dz)/\rho}$ is the so-called friction velocity.
+However, in the current settings, we are not able to satisfy Eqs. \ref{MOST1} and \ref{MOST2} directly, since the specification of $K$ has to be done a-priori, and $u_*$ depends on the solution. 
+This is the main weakness of linear approaches.
+The only way to enforce Eqs.
+\ref{MOST1} and \ref{MOST2} would be to apply a procedure in which $K(z)$ is iteratively updated to match the MO similarity relations.
+Based on recent direct (DNS) and large-eddy simulation (LES) results (not shown) we make the additional assumption that $h$ is located in the neighborhood of the first zero of the $u$ velocity profile, well above $z_j$ but within the dynamic and thermal boundary layers ($h$ would be at the lower boundary of the return flow).
+Knowledge of $K(z_0),dK(z_0)/dz$ and $h$ allows to univocally define $K(z)= A(z + \epsilon)(z-\zeta)^2$ one can therefore specify the surface value and its derivative $K(0), dK(0)/dz$ and 
+Under such restrictive (but realistic) assumption it is possible to show that the $H$ parameter in
+
+Despite the restrictive form of the model parameter, which might limit the applicability of the solution in certain contexts, the model
+
 \section{Examples}
@@
 The constant-$K$ value is fixed to $K^+_{\mathrm{A2}} = \max(K_{\mathrm{A1}}^+)/3$. 
-Profiles for N1 are derived by solving monolithically the system of ODEs defined by Eqs.
-\ref{eqn1u_norm} and \ref{eqn1b_norm}, adopting a second-order accurate centered finite difference discretization with over $40,000$ collocation points and stretching the grid via a quadratic coordinate transform (at such resolution profiles are invariant to further refinements down to machine precision).
+Profiles for N1 are derived as direct numerical solution the system of ODEs defined by Eqs.
+\ref{eqn1u_norm} and \ref{eqn1b_norm}, where a second-order accurate centered finite difference discretization is adopted with over $40,000$ collocation points and stretching the grid via a quadratic coordinate transform (at such resolution profiles are invariant to further refinements down to machine precision).
 The excellent match between A1 and N1 certifies the quality of results for both methods. 
@@
 %\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{/Users/mg/Phd/papers/bib_files/library}
+\bibliography{/Users/mg/Phd/papers/bib_files/library}
 
-\begin{thebibliography}{26}
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{{#1}}
-\providecommand{\urlprefix}{URL }
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-  \urlstyle{rm}\Url}\fi
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem[{Chu(1987)}]{Chu1987}
-Chu PC (1987) {An instability theory of ice-air interaction for the formation
-  of ice edge bands}. Journal of Geophysical Research 92(7):6966,
-  \doi{10.1029/JC092iC07p06966}
-
-\bibitem[{Egger(1985)}]{Egger1985}
-Egger J (1985) {Slope Winds and the Axisymmetric Circulation over Antarctica}.
-  Journal of the Atmospheric Sciences 42:1859--1867,
-  \doi{10.1175/1520-0469(1985)042<1859:SWATAC>2.0.CO;2}
-
-\bibitem[{Fedorovich and Shapiro(2009{\natexlab{a}})}]{Fedorovich2009d}
-Fedorovich E, Shapiro A (2009{\natexlab{a}}) {Structure of numerically
-  simulated katabatic and anabatic flows along steep slopes}. Acta Geophysica
-  57(4):981--1010, \doi{10.2478/s11600-009-0027-4},
-  \urlprefix\url{http://www.springerlink.com/index/10.2478/s11600-009-0027-4}
-
-\bibitem[{Fedorovich and Shapiro(2009{\natexlab{b}})}]{Fedorovich2009}
-Fedorovich E, Shapiro A (2009{\natexlab{b}}) {Turbulent natural convection
-  along a vertical plate immersed in a stably stratified fluid}. Journal of
-  Fluid Mechanics 636:41, \doi{10.1017/S0022112009007757}
-
-\bibitem[{Grisogono and Oerlemans(2001)}]{grisogono2001katabatic}
-Grisogono B, Oerlemans J (2001) {Katabatic Flow: Analytic Solution for
-  Gradually Varying Eddy Diffusivities}. Journal of the Atmospheric Sciences
-  58(21):3349--3354,
-  \doi{http://dx.doi.org/10.1175/1520-0469(2001)058<3349:KFASFG>2.0.CO;2}
-
-\bibitem[{Grisogono and Oerlemans(2002)}]{Grisogono2002}
-Grisogono B, Oerlemans J (2002) {Justifying the WKB approximation in pure
-  katabatic flows}. Tellus, A 54(5):453--462,
-  \doi{10.1034/j.1600-0870.2002.201399.x}
-
-\bibitem[{Gutman(1983)}]{gutman_1983}
-Gutman LN (1983) {On the theory of the katabatic slope wind}. Tellus, A
-  35(3):332--335, \doi{10.3402/tellusa.v35i3.11434}
-
-\bibitem[{Gutman and Malbakhov(1964)}]{Gutman1964}
-Gutman LN, Malbakhov VM (1964) {On the Theory of the Katabatic Winds of
-  Antarctica}. University of Melbourne, Meteorology Department
-
-\bibitem[{Lykosov and Gutman(1972)}]{Lykosov_1972}
-Lykosov VN, Gutman LN (1972) {Turbulent boundary layer above a sloping
-  inderlying surface}. Proceedings of the USSR Academy of Sciences 8:799--809,
-  \urlprefix\url{papers2://publication/uuid/B2EC0692-4251-4224-8185-A1AE8D9B00E9}
-
-\bibitem[{Mahrt(1998)}]{Mahrt1998}
-Mahrt L (1998) {Stratified Atmospheric Boundary Layers and Breakdown of
-  Models}. In: Theoretical and Computational Fluid Dynamics, vol~11, pp
-  263--279, \doi{10.1007/s001620050093},
-  \urlprefix\url{http://link.springer.com/10.1007/s001620050093}
-
-\bibitem[{Monti et~al.(2002)Monti, Fernando, Princevac, Chan, Kowalewski, and
-  Pardyjak}]{Monti2002}
-Monti P, Fernando HJS, Princevac M, Chan WC, Kowalewski TA, Pardyjak ER (2002)
-  {Observations of Flow and Turbulence in the Nocturnal Boundary Layer over a
-  Slope}. Journal of the Atmospheric Sciences 59:2513--2534,
-  \doi{10.1175/1520-0469(2002)059<2513:OOFATI>2.0.CO;2}
-
-\bibitem[{Morse and Feshbach(1953)}]{Morse1954a}
-Morse PM, Feshbach H (1953) {Methods of Theoretical Physics}. McGraw-Hill
-
-\bibitem[{Nadeau et~al.(2013)Nadeau, Pardyjak, Higgins, and
-  Parlange}]{Nadeau2012}
-Nadeau DF, Pardyjak ER, Higgins CW, Parlange MB (2013) {Similarity Scaling Over
-  a Steep Alpine Slope}. Boundary-Layer Meteorology 147(3):401--419,
-  \doi{10.1007/s10546-012-9787-5},
-  \urlprefix\url{http://link.springer.com/10.1007/s10546-012-9787-5}
-
-\bibitem[{Nappo and Shankar(1987)}]{NAPPO1987}
-Nappo CJ, Shankar RK (1987) {A model study of pure katabatic flows}. Tellus A
-  39(1):61--71, \doi{10.3402/tellusa.v39i1.11740},
-  \urlprefix\url{http://onlinelibrary.wiley.com/doi/10.1111/j.1600-0870.1987.tb00289.x/abstract}
-
-\bibitem[{Nylen et~al.(2004)Nylen, {Andrew G. F.}, and Doran}]{Nylen2004b}
-Nylen TH, {Andrew G F}, Doran PT (2004) {Climatology of katabatic winds in the
-  McMurdo dry valleys, southern Victoria Land, Antarctica}. Journal of
-  Geophysical Research 109:1--9, \doi{10.1029/2003JD003937}
-
-\bibitem[{O'Brien(1970)}]{O'Brien1970}
-O'Brien JJ (1970) {A Note on the Vertical Structure of the Eddy Exchange
-  Coefficient in the Planetary Boundary Layer}. Journal of the Atmospheric
-  Sciences 27:1213--1215,
-  \doi{10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2},
-  \urlprefix\url{http://dx.doi.org/10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2}
-
-\bibitem[{Oerlemans(1998)}]{Oerlemans1998}
-Oerlemans J (1998) {The atmospheric boundary layer over melting glaciers}. In:
-  Clear and Cloudy Boundary Layers, vol~48, Royal Netherlands Academy of Arts
-  and Sciences, pp 129--153,
-  \urlprefix\url{http://igitur-archive.library.uu.nl/phys/2007-0716-203217/oerlemans\_07\_atmosphericboundarylayer.pdf}
-
-\bibitem[{Oerlemans and Vugts(1993)}]{Oerlemans1993}
-Oerlemans J, Vugts HF (1993) {A Meteorological Experiment in the Melting Zone
-  of the Greenland Ice Sheet}. Bulletin of the American Meteorological Society
-  74(3):355--365, \doi{10.1175/1520-0477(1993)074<0355:AMEITM>2.0.CO;2}
-
-\bibitem[{Oldroyd et~al.(2014)Oldroyd, Katul, Pardyjak, and
-  Parlange}]{Oldroyd2014}
-Oldroyd HJ, Katul G, Pardyjak ER, Parlange MB (2014) {Momentum balance of
-  katabatic flow on steep slopes covered with short vegetation}. Geophysical
-  Research Letters 41:4761--4768, \doi{10.1002/2014GL060313}
-
-\bibitem[{Parish(1992)}]{Parish1992}
-Parish TR (1992) {On the Role of Antarctic Katabatic Winds in Forcing
-  Large-Scale Tropospheric Motions}. Journal of the Atmospheric Sciences
-  49:1374--1385, \doi{10.1175/1520-0469(1992)049<1374:OTROAK>2.0.CO;2}
-
-\bibitem[{Parish and Bromwich(1998)}]{Parish1998}
-Parish TR, Bromwich DH (1998) {A Case Study of Antarctic Katabatic Wind
-  Interaction with Large-Scale Forcing}. Monthly Weather Review 126:199--209,
-  \doi{10.1175/1520-0493(1998)126<0199:ACSOAK>2.0.CO;2}
-
-\bibitem[{Prandtl(1942)}]{Prandtl}
-Prandtl L (1942) {F\"{u}hrer durch die Str\"{o}mungslehre}. Vieweg \& Sohn,
-  Braunschweig
-
-\bibitem[{Shapiro and Fedorovich(2004{\natexlab{a}})}]{Shapiro2004a}
-Shapiro A, Fedorovich E (2004{\natexlab{a}}) {Prandtl number dependence of
-  unsteady natural convection along a vertical plate in a stably stratified
-  fluid}. International Journal of Heat and Mass Transfer 47(22):4911--4927,
-  \doi{10.1016/j.ijheatmasstransfer.2004.04.035},
-  \urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0017931004002157}
-
-\bibitem[{Shapiro and Fedorovich(2004{\natexlab{b}})}]{Shapiro2004}
-Shapiro A, Fedorovich E (2004{\natexlab{b}}) {Unsteady convectively driven flow
-  along a vertical plate immersed in a stably stratified fluid}. Journal of
-  Fluid Mechanics 498:333--352, \doi{10.1017/S0022112003006803},
-  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112003006803}
-
-\bibitem[{Shapiro and Fedorovich(2007)}]{Shapiro2007}
-Shapiro A, Fedorovich E (2007) {Katabatic flow along a differentially cooled
-  sloping surface}. Journal of Fluid Mechanics 571:149,
-  \doi{10.1017/S0022112006003302},
-  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112006003302}
-
-\bibitem[{Spalart et~al.(2011)Spalart, Strelets, and
-  Garbaruk}]{Burkholder2011a}
-Spalart P, Strelets M, Garbaruk A (2011) {Quality and Reliability of Large-Eddy
-  Simulations II}. In: Evaluating Subgrid-ScaleModels for Large-Eddy Simulation
-  of Turbulent Katabatic Flow, vol~16, pp 253--267,
-  \doi{10.1007/978-94-007-0231-8},
-  \urlprefix\url{http://www.springerlink.com/index/10.1007/978-94-007-0231-8}
-
-\end{thebibliography}
+%\begin{thebibliography}{26}
+%\providecommand{\natexlab}[1]{#1}
+%\providecommand{\url}[1]{{#1}}
+%\providecommand{\urlprefix}{URL }
+%\expandafter\ifx\csname urlstyle\endcsname\relax
+%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
+%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
+%  \urlstyle{rm}\Url}\fi
+%\providecommand{\eprint}[2][]{\url{#2}}
+%
+%\bibitem[{Bender and Orszag(1999)}]{Bender1999}
+%Bender CM, Orszag SA (1999) {Advanced Mathematical Methods for Scientists and
+%  Engineers I}. Springer New York, New York, NY,
+%  \doi{10.1007/978-1-4757-3069-2},
+%  \urlprefix\url{http://eprints.ucl.ac.uk/70187/
+%  http://link.springer.com/10.1007/978-1-4757-3069-2}
+%  
+%\bibitem[{Chu(1987)}]{Chu1987}
+%Chu PC (1987) {An instability theory of ice-air interaction for the formation
+%  of ice edge bands}. Journal of Geophysical Research 92(7):6966,
+%  \doi{10.1029/JC092iC07p06966}
+%
+%\bibitem[{Egger(1985)}]{Egger1985}
+%Egger J (1985) {Slope Winds and the Axisymmetric Circulation over Antarctica}.
+%  Journal of the Atmospheric Sciences 42:1859--1867,
+%  \doi{10.1175/1520-0469(1985)042<1859:SWATAC>2.0.CO;2}
+%
+%\bibitem[{Fedorovich and Shapiro(2009{\natexlab{a}})}]{Fedorovich2009d}
+%Fedorovich E, Shapiro A (2009{\natexlab{a}}) {Structure of numerically
+%  simulated katabatic and anabatic flows along steep slopes}. Acta Geophysica
+%  57(4):981--1010, \doi{10.2478/s11600-009-0027-4},
+%  \urlprefix\url{http://www.springerlink.com/index/10.2478/s11600-009-0027-4}
+%
+%\bibitem[{Fedorovich and Shapiro(2009{\natexlab{b}})}]{Fedorovich2009}
+%Fedorovich E, Shapiro A (2009{\natexlab{b}}) {Turbulent natural convection
+%  along a vertical plate immersed in a stably stratified fluid}. Journal of
+%  Fluid Mechanics 636:41, \doi{10.1017/S0022112009007757}
+%
+%\bibitem[{Grisogono and Oerlemans(2001)}]{grisogono2001katabatic}
+%Grisogono B, Oerlemans J (2001) {Katabatic Flow: Analytic Solution for
+%  Gradually Varying Eddy Diffusivities}. Journal of the Atmospheric Sciences
+%  58(21):3349--3354,
+%  \doi{http://dx.doi.org/10.1175/1520-0469(2001)058<3349:KFASFG>2.0.CO;2}
+%
+%\bibitem[{Grisogono and Oerlemans(2002)}]{Grisogono2002}
+%Grisogono B, Oerlemans J (2002) {Justifying the WKB approximation in pure
+%  katabatic flows}. Tellus, A 54(5):453--462,
+%  \doi{10.1034/j.1600-0870.2002.201399.x}
+%
+%\bibitem[{Gutman(1983)}]{gutman_1983}
+%Gutman LN (1983) {On the theory of the katabatic slope wind}. Tellus, A
+%  35(3):332--335, \doi{10.3402/tellusa.v35i3.11434}
+%
+%\bibitem[{Gutman and Malbakhov(1964)}]{Gutman1964}
+%Gutman LN, Malbakhov VM (1964) {On the Theory of the Katabatic Winds of
+%  Antarctica}. University of Melbourne, Meteorology Department
+%
+%\bibitem[{Lykosov and Gutman(1972)}]{Lykosov_1972}
+%Lykosov VN, Gutman LN (1972) {Turbulent boundary layer above a sloping
+%  inderlying surface}. Proceedings of the USSR Academy of Sciences 8:799--809,
+%  \urlprefix\url{papers2://publication/uuid/B2EC0692-4251-4224-8185-A1AE8D9B00E9}
+%
+%\bibitem[{Mahrt(1998)}]{Mahrt1998}
+%Mahrt L (1998) {Stratified Atmospheric Boundary Layers and Breakdown of
+%  Models}. In: Theoretical and Computational Fluid Dynamics, vol~11, pp
+%  263--279, \doi{10.1007/s001620050093},
+%  \urlprefix\url{http://link.springer.com/10.1007/s001620050093}
+%
+%\bibitem[{Monti et~al.(2002)Monti, Fernando, Princevac, Chan, Kowalewski, and
+%  Pardyjak}]{Monti2002}
+%Monti P, Fernando HJS, Princevac M, Chan WC, Kowalewski TA, Pardyjak ER (2002)
+%  {Observations of Flow and Turbulence in the Nocturnal Boundary Layer over a
+%  Slope}. Journal of the Atmospheric Sciences 59:2513--2534,
+%  \doi{10.1175/1520-0469(2002)059<2513:OOFATI>2.0.CO;2}
+%
+%\bibitem[{Morse and Feshbach(1953)}]{Morse1954a}
+%Morse PM, Feshbach H (1953) {Methods of Theoretical Physics}. McGraw-Hill
+%
+%\bibitem[{Nadeau et~al.(2013)Nadeau, Pardyjak, Higgins, and
+%  Parlange}]{Nadeau2012}
+%Nadeau DF, Pardyjak ER, Higgins CW, Parlange MB (2013) {Similarity Scaling Over
+%  a Steep Alpine Slope}. Boundary-Layer Meteorology 147(3):401--419,
+%  \doi{10.1007/s10546-012-9787-5},
+%  \urlprefix\url{http://link.springer.com/10.1007/s10546-012-9787-5}
+%
+%\bibitem[{Nappo and Shankar(1987)}]{NAPPO1987}
+%Nappo CJ, Shankar RK (1987) {A model study of pure katabatic flows}. Tellus A
+%  39(1):61--71, \doi{10.3402/tellusa.v39i1.11740},
+%  \urlprefix\url{http://onlinelibrary.wiley.com/doi/10.1111/j.1600-0870.1987.tb00289.x/abstract}
+%
+%\bibitem[{Nylen et~al.(2004)Nylen, {Andrew G. F.}, and Doran}]{Nylen2004b}
+%Nylen TH, {Andrew G F}, Doran PT (2004) {Climatology of katabatic winds in the
+%  McMurdo dry valleys, southern Victoria Land, Antarctica}. Journal of
+%  Geophysical Research 109:1--9, \doi{10.1029/2003JD003937}
+%
+%\bibitem[{O'Brien(1970)}]{O'Brien1970}
+%O'Brien JJ (1970) {A Note on the Vertical Structure of the Eddy Exchange
+%  Coefficient in the Planetary Boundary Layer}. Journal of the Atmospheric
+%  Sciences 27:1213--1215,
+%  \doi{10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2},
+%  \urlprefix\url{http://dx.doi.org/10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2}
+%
+%\bibitem[{Oerlemans(1998)}]{Oerlemans1998}
+%Oerlemans J (1998) {The atmospheric boundary layer over melting glaciers}. In:
+%  Clear and Cloudy Boundary Layers, vol~48, Royal Netherlands Academy of Arts
+%  and Sciences, pp 129--153,
+%  \urlprefix\url{http://igitur-archive.library.uu.nl/phys/2007-0716-203217/oerlemans\_07\_atmosphericboundarylayer.pdf}
+%
+%\bibitem[{Oerlemans and Vugts(1993)}]{Oerlemans1993}
+%Oerlemans J, Vugts HF (1993) {A Meteorological Experiment in the Melting Zone
+%  of the Greenland Ice Sheet}. Bulletin of the American Meteorological Society
+%  74(3):355--365, \doi{10.1175/1520-0477(1993)074<0355:AMEITM>2.0.CO;2}
+%
+%\bibitem[{Oldroyd et~al.(2014)Oldroyd, Katul, Pardyjak, and
+%  Parlange}]{Oldroyd2014}
+%Oldroyd HJ, Katul G, Pardyjak ER, Parlange MB (2014) {Momentum balance of
+%  katabatic flow on steep slopes covered with short vegetation}. Geophysical
+%  Research Letters 41:4761--4768, \doi{10.1002/2014GL060313}
+%
+%\bibitem[{Parish(1992)}]{Parish1992}
+%Parish TR (1992) {On the Role of Antarctic Katabatic Winds in Forcing
+%  Large-Scale Tropospheric Motions}. Journal of the Atmospheric Sciences
+%  49:1374--1385, \doi{10.1175/1520-0469(1992)049<1374:OTROAK>2.0.CO;2}
+%
+%\bibitem[{Parish and Bromwich(1998)}]{Parish1998}
+%Parish TR, Bromwich DH (1998) {A Case Study of Antarctic Katabatic Wind
+%  Interaction with Large-Scale Forcing}. Monthly Weather Review 126:199--209,
+%  \doi{10.1175/1520-0493(1998)126<0199:ACSOAK>2.0.CO;2}
+%
+%\bibitem[{Prandtl(1942)}]{Prandtl}
+%Prandtl L (1942) {F\"{u}hrer durch die Str\"{o}mungslehre}. Vieweg \& Sohn,
+%  Braunschweig
+%
+%\bibitem[{Shapiro and Fedorovich(2004{\natexlab{a}})}]{Shapiro2004a}
+%Shapiro A, Fedorovich E (2004{\natexlab{a}}) {Prandtl number dependence of
+%  unsteady natural convection along a vertical plate in a stably stratified
+%  fluid}. International Journal of Heat and Mass Transfer 47(22):4911--4927,
+%  \doi{10.1016/j.ijheatmasstransfer.2004.04.035},
+%  \urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0017931004002157}
+%
+%\bibitem[{Shapiro and Fedorovich(2004{\natexlab{b}})}]{Shapiro2004}
+%Shapiro A, Fedorovich E (2004{\natexlab{b}}) {Unsteady convectively driven flow
+%  along a vertical plate immersed in a stably stratified fluid}. Journal of
+%  Fluid Mechanics 498:333--352, \doi{10.1017/S0022112003006803},
+%  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112003006803}
+%
+%\bibitem[{Shapiro and Fedorovich(2007)}]{Shapiro2007}
+%Shapiro A, Fedorovich E (2007) {Katabatic flow along a differentially cooled
+%  sloping surface}. Journal of Fluid Mechanics 571:149,
+%  \doi{10.1017/S0022112006003302},
+%  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112006003302}
+%
+%\bibitem[{Spalart et~al.(2011)Spalart, Strelets, and
+%  Garbaruk}]{Burkholder2011a}
+%Spalart P, Strelets M, Garbaruk A (2011) {Quality and Reliability of Large-Eddy
+%  Simulations II}. In: Evaluating Subgrid-ScaleModels for Large-Eddy Simulation
+%  of Turbulent Katabatic Flow, vol~16, pp 253--267,
+%  \doi{10.1007/978-94-007-0231-8},
+%  \urlprefix\url{http://www.springerlink.com/index/10.1007/978-94-007-0231-8}
+%
+%\end{thebibliography}
 

### 2015-11-03 paper_BLM.tex
latest version

@@
 where $z$ denotes the normal-to-slope coordinate directions, $u$ is the downslope velocity, $b$ is buoyancy, $N$ is the buoyancy frequency characterizing the system (related to the background stratification), $\alpha$ is the slope angle and $K_M$ and $K_H$ denote the eddy viscosity and diffusivity (an eddy viscosity/diffusivity model has been used to parametrize turbulent fluxes of momentum and buoyancy).
-Equations are defined in $z \in \ [0,\infty)$ with boundary conditions $u(0)=0$, $u(z \rightarrow \infty) = 0$, $b(0)=b_s$ and $b(z \rightarrow \infty) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).
+Equations are defined in $z \in \ [z_0,\infty)$ with boundary conditions $u(z_0)=0$, $u(z \rightarrow \infty) = 0$, $b(z_0)=b_s$ and $b(z \rightarrow \infty) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).
 
@@
 Assuming eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz.
-$K(z) = A (z + \epsilon)(z-\zeta)^2$, where $\epsilon>0$ and $\zeta>H$ are parameters that we introduce in order to shift the zeroes of $K$ outside the interval of integration $[0,H]$, assuming $Pr=1$ (i.e.
+$K(z) = A z(z-\zeta)^2$, where $\zeta>H$, $Pr=1$ (i.e.
 $K_M=K_H=K$) and assigning a length, velocity and buoyancy scale $L= (N \sin{\alpha})/ A$, $U=b_s N^{-1}$ and $B=b_s$ respectively, Eqs.
@@
 \begin{align}
-	\overline{u} & = d( \overline{K} d\overline{b}/d\overline{z} )/d\overline{z}, && \mathrm{in}  \ [0,\overline{H}]
+	\overline{u} & = d( \overline{K} d\overline{b}/d\overline{z} )/d\overline{z}, && \mathrm{in}  \ [z_0,\overline{H}]
 	\label{eqn1u_norm} \\
 	%
-	\overline{b} & = -d( \overline{K} d\overline{u}/d\overline{z} )/d\overline{z}, &&\mathrm{in}  \ [0,\overline{H}]
+	\overline{b} & = -d( \overline{K} d\overline{u}/d\overline{z} )/d\overline{z}, &&\mathrm{in}  \ [z_0,\overline{H}]
 	\label{eqn1b_norm}
@@
 %
-where $\overline{K} = (\overline{z} + \overline{\epsilon})(\overline{z}-\overline{\zeta})^2$ is the normalized eddy viscosity/diffusivity, $\overline{z}=zL^{-1}$, $\overline{u} = uU^{-1}$, $\overline{b}=b B^{-1}$, with boundary conditions $\overline{u}(0)=0$, $\overline{u}(\overline{H}) = 0$, $\overline{b}(0)=\pm 1$ and $\overline{b}(\overline{H}) = 0$.
+where $\overline{K} = \overline{z}(\overline{z}-\overline{\zeta})^2$ is the normalized eddy viscosity/diffusivity, $\overline{z}=zL^{-1}$, $\overline{u} = uU^{-1}$, $\overline{b}=b B^{-1}$, with boundary conditions $\overline{u}(z_0)=0$, $\overline{u}(\overline{H}) = 0$, $\overline{b}(z_0)=\pm 1$ and $\overline{b}(\overline{H}) = 0$.
 Overbars $\overline{(\cdot)}$ will be omitted hereafter.
@@
 \begin{equation}
-	i \cdot f =  d(  K df/dz )/dz \hspace{1cm} \mathrm{in}  \ [0,H],
+	i \cdot f =  d(  K df/dz )/dz \hspace{1cm} \mathrm{in}  \ [z_0,H],
 	\label{ode}
@@
 %
-with boundary conditions $f(0)=\pm 1$ and $f(H) = 0$.
+with boundary conditions $f(z_0)=\pm 1$ and $f(H) = 0$.
 This technique for the decoupling of the system of Eqs. \ref{eqn1u_norm} and \ref{eqn1b_norm} is based on an ad hoc diagonalization.
@@
 %
-where $(\cdot)' = \frac{\partial (\cdot)}{\partial z}$, $P(z)=(K)'/K$ and $Q(z)=1/(i K)$.
-Second, it is an easy computation to show that rewriting Eq.
-\ref{can_form} for $y = \frac{z + \epsilon}{H + \epsilon + \zeta}
+where $(\cdot)' = \frac{\partial (\cdot)}{\partial z}$, $P(z)=(K)'/K$ and $Q(z)=1/(i K)$. Second, it is an easy computation to show that rewriting Eq. \ref{can_form} for $y = \frac{z }{\zeta}
 $ results in
@@
 %
-where $(\cdot)' = \frac{\partial (\cdot)}{\partial y}$, $\widetilde{P}(y)=\gamma'(y)/\gamma(y)$ and $\widetilde{Q}(y)=1/( i \cdot (H+\epsilon+\zeta) \gamma(y))$, with $\gamma(y)=y(y-1)^2$.
+where $(\cdot)' = \frac{\partial (\cdot)}{\partial y}$, $\widetilde{P}(y)=\gamma'(y)/\gamma(y)$ and $\widetilde{Q}(y)=1/( i \cdot \zeta \gamma(y))$, with $\gamma(y)=y(y-1)^2$.
 Eq. \ref{can_form_sec} is a second order ODE with three regular singular points at $y = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
@@
 \begin{equation*}
-	x^2+x+1/( i (H+ \epsilon + \zeta))=0.
+	x^2+x+1/( i \zeta)=0.
 \end{equation*}
@@
 Further, as stated in the preceeding section, we assume eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz.
-$K = A(z + \epsilon)(z-\zeta)^2$, where $\epsilon>0$ can be tuned to provide the desired value of eddy viscosity / diffusivity at the wall, whereas $\zeta > H$ controls both shape and magnitude of $K$.
+$K = Az(z-\zeta)^2$, where $A$ is a prefactor and $\zeta > H$ controls both shape and magnitude of $K$.
 The O'Brien model has often been used in studies of stable boundary layers, see for instance \citet{pielke1984mesoscale} and \citet{Stull1988}, and a generalized O'Brien model was also recently adopted in \citet{grisogono2001katabatic} to study slope flows.
@@
 %
-In addition, assuming Monin-Obukhov similarity theory to hold for the near wall regions (which is itself a subject of great debate), one would ideally specify $K(z)$ in order to satisfy:
+In addition, assuming Monin-Obukhov similarity theory to hold for the near wall regions (which is itself a subject of debate), one would ideally specify $K(z)$ in order to satisfy:
 %
@@
 \begin{align}
-   K(z) & = \kappa u_* z/[1+\Phi(z)] & z \in [z_0,z_s], \label{MOST1}\\
+   K(z) & = \kappa u_* z & z \in [z_0,z_s], \label{MOST1}\\
    K(z) & = f(u_*,z) \ | \ d^2f/dz^2 < 0 & z \in (z_s,H], \label{MOST2}
@@
 \end{linenomath*}
+%%
+%\begin{linenomath*}
+%\begin{subequations}
+%\begin{align}
+%   K(z) & = \kappa u_* z/[1+\Phi(z)] & z \in [z_0,z_s], \label{MOST1}\\
+%   K(z) & = f(u_*,z) \ | \ d^2f/dz^2 < 0 & z \in (z_s,H], \label{MOST2}
+%\end{align}
+%\end{subequations}
+%\end{linenomath*}
 %
-where $z_s$ is the upper boundary of the constant-flux layer, $\Phi(z)$ is a stability correction function, $\kappa$ is the Von K\'arm\'an constant, and $u_* = \sqrt{K(du/dz)/\rho}$ is the so-called friction velocity.
-However, in the current settings, we are not able to satisfy Eqs. \ref{MOST1} and \ref{MOST2} directly, since the specification of $K$ has to be done a-priori, and $u_*$ depends on the solution. 
-This is the main weakness of linear approaches.
-The only way to enforce Eqs.
-\ref{MOST1} and \ref{MOST2} would be to apply a procedure in which $K(z)$ is iteratively updated to match the MO similarity relations.
-Based on recent direct (DNS) and large-eddy simulation (LES) results (not shown) we make the additional assumption that $h$ is located in the neighborhood of the first zero of the $u$ velocity profile, well above $z_j$ but within the dynamic and thermal boundary layers ($h$ would be at the lower boundary of the return flow).
-Knowledge of $K(z_0),dK(z_0)/dz$ and $h$ allows to univocally define $K(z)= A(z + \epsilon)(z-\zeta)^2$ one can therefore specify the surface value and its derivative $K(0), dK(0)/dz$ and 
-Under such restrictive (but realistic) assumption it is possible to show that the $H$ parameter in
+where $z_s$ is the upper boundary of the constant-flux layer, $\kappa$ is the Von K\'arm\'an constant, and $u_* = \kappa z (du/dz)|_{z_0}$, is the so-called friction velocity.
+Based on recent direct (DNS) and large-eddy simulation (LES) results (not shown) we make the additional assumption that $h$ is located in the neighborhood of the first zero of the $u$ velocity profile, well above $z_j$ but within the dynamic and thermal boundary layers (under such constraint $h$ identifies the lower boundary of the return flow).
+We will show hereafter that the solution is poorly sensitive on the exact value of $h$, as long as the resulting domain height $H<\zeta$ is large enough to accomodate the dynamic and thermal boundary layers.
+Knowledge of $dK/dz|_{z=z_0}$ and $h$ allows to univocally specify $K(z)= Az(z-\zeta)^2$. A possible alternative would be to specify $dK/dz|_{z=z_0}$ and $\max{(K)}$. 
+The size of the integration interval should be chosen as large as possible, under the constraint $H<\zeta$.
+Throughout the study we will set $H = \zeta-\zeta/100$, which allows to fully represent the dynamic and thermal boundary layers over a broad range of $z_0$ values.
+Note that in general it is not possible to satisfy Eqs. \ref{MOST1} directly, since the specification of $K$ has to be done a-priori, and $u_*$ depends on the solution. 
+The chosen normalization allows to overcome this limitation, and highlights the linear dependence of the length scales of the flow on $u_*$ ($A \propto u_* \propto L)$.
+One could therefore first solve for $\overline{u}$ and $\overline{b}$, and then re-dimensionalize the problem, imposing $A=\kappa u_* / \zeta^2$ thus resulting in $K(z)=\kappa u_* z$, in agreement with Eq.
+\ref{MOST1}.
 
-Despite the restrictive form of the model parameter, which might limit the applicability of the solution in certain contexts, the model
+Despite the restrictive form of the model parameter $K(z)$, the formulation allows for exact integration of Eqs.
+\ref{eqn1u} and \ref{eqn1b}, thus providing a useful reference to test approximate solutions such as the WKB \citep{grisogono2001katabatic} and the dependence of the flow on the additional model parameter $z_0$.
+Further, the formulation can be used to validate numerical solutions of the Prandtl model equations (Eqs.
+\ref{eqn1u} and \ref{eqn1b}).
 
@@
    \begin{center}
-      \includegraphics[width= 70.0mm]{./u-b_log}
+      \includegraphics[width= 70.0mm]{./comparison_normalized_analytic_solutions_z0=1e-05}
       \caption{Comparison of the new analytic solution (A1) against the constant-$K$ (A2), the WKB (A3) and a numerical $1D$ solution (N1).
-Analytic profiles of normalized velocity $(u^+)$ are denoted with dot-dashed lines whereas analytic profiles of normalized buoyancy $(b^+)$ are denoted by dashed lines.
-Here $K^+ = A^+ \cdot (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$ where $A^+=6.75 e-4$, $\epsilon^+ =1.5 \times 10^{-3}$ and $H^+ = 10$.
+Analytic profiles of normalized velocity $(\overline{u})$ are denoted with dot-dashed lines whereas analytic profiles of normalized buoyancy $(\overline{b})$ are denoted by dashed lines.
+Here $\overline{z}_0 = 0.00001$ and $\overline{\zeta} = 0.1$.
 A corresponding dimensional profile is characterized by $\max{(K)} = 0.1 \ \mathrm{m^2s^{-1}}$ and $K(z=0) = 10^{-5} \ \mathrm{m^2s^{-1}}$, in agreement with common atmospheric values.}
@@
 %
-In Fig. \ref{fig1} we compare the new analytic solution (A1 in the following) against the constant-$K$ (A2), the WKB (A3) and a numerical solution (N1).
+In Fig.
+\ref{fig1} we compare the new analytic solution (A1 in the following) against the constant-$K$ (A2), the WKB (A3) and a numerical solution (N1), for a chosen $z_0,\zeta$.
+$\zeta$ is specified so that $h$ is located at the first zero of the $u(z)$ profile.
 The constant-$K$ value is fixed to $K^+_{\mathrm{A2}} = \max(K_{\mathrm{A1}}^+)/3$. 
@@
 The excellent match between A1 and N1 certifies the quality of results for both methods. 
-In comparison to its analytical counterparts, A1 shows a remarkably strong inversion in the near surface regions $(z^+ <1)$, suggesting overdiffusive behaviour of both A2 and A3, which are incapable of providing such strong buoyancy gradients.
+A1 shows a remarkably strong inversion in the near surface regions $(z^+ <1)$, when compared against its analytical counterparts, suggesting an overdiffusive behaviour of both A2 and A3. 
 For instance, normalized surface buoyancy gradients of simulation A1 are over an order of magnitude larger than those of A2 $( (db/dz)^+_\mathrm{A1}/(db/dz)^+_\mathrm{A2} = \mathcal{O}(10)$ as $z^+ \rightarrow 0$).

### 2016-06-23 materials_methods.tex
pre-review

\section{Materials and methods}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical algorithm}

%\subsubsection{Equations of motion and discretization} 
The isothermal filtered Navier-Stokes equations are solved in their rotational form \citep{Orszag1975}, to ensure conservation of mass and kinetic energy: 
%
\begin{equation}
\begin{cases}
   \frac{\partial \tilde{u}_i}{\partial t} 
      + \tilde{u}_j ( \frac{\partial \tilde{u}_i}{\partial x_j} 
      - \frac{\partial \tilde{u}_j}{\partial x_i} ) 
      = 
      - \frac{\partial \tilde{\pi}}{\partial x_i} 
      - \frac{\partial \tau_{ij}^{SGS}}{\partial x_j} 
      - \Pi_1  + \tilde{f}_i^{\Gamma_{\mathrm{b}}} & \text{in $\Omega \times [0,T]$} \, , \\
   	\frac{\partial \tilde{u}_i}{\partial x_i} =0 & \text{in $\Omega \times [0,T]$} \, , \\
	\frac{\partial \tilde{u}}{\partial z} = \frac{\partial \tilde{v}}{\partial z} = 
	\tilde{w} = 0 & \text{in $\Gamma_{\mathrm{top}} \times [0,T]$} \, , \\
	(\mathbf{\tilde{u}} \cdot \mathbf{\tilde{n}}) \mathbf{\tilde{n}} = \mathbf{\tilde{u}}_N = 0 & \text{in $\Gamma_{\mathrm{b}} \times [0,T]$} \, , \\
	\mathbf{\tilde{t}} = - \left( \frac{ \kappa ( \mathbf{\tilde{u}} - \mathbf{\tilde{u}}_N )}{\ln{(1+\Delta/z_0)}} \right)^2 & \text{in $\Gamma_{\mathrm{b}} \times [0,T]$} \, .
	\label{eq_motions}
\end{cases}
\end{equation}
%
Here $\tilde{u}_i$ are the filtered velocity components in the three coordinate directions, $\tilde{\pi}$ is a modified filtered pressure field, namely $  \tilde{\pi} = \frac{\tilde{p}}{\rho} + \frac{1}{3}\tau_{ii}^{SGS} + \frac{1}{2}\tilde{u}_i\tilde{u}_i $, $\rho$ is a reference density, $\tau_{ij}^{SGS}$ is the subgrid-scale (SGS) stress tensor (resulting from the filtering operation \citep{Pope2000a}), $ \Pi_1 = \frac{1}{\rho} \frac{\partial \tilde{p}_{\infty}}{\partial x_i}\delta_{i1} < 0$ is a pressure gradient that is introduced to drive the flow, and $\tilde{f}_i^{\Gamma_{\mathrm{b}}}$ is a forcing term that is used to impose the desired boundary condition at the surface location. $\tilde{f}_i^{\Gamma_{\mathrm{b}}}$ has a finite value at the buildings interface $(\Gamma_{\mathrm{b}})$ and is zero elsewhere.
Further, $\mathbf{\tilde{t}}$ is the stress vector at the surface location, $\mathbf{\tilde{u}}_N$ is the normal-to-surface velocity vector, $\Delta = (dx \times dy \times dz)^{1/3}$ and $z_0$ is the hydrodynamic roughness length parameter.
The argument of the $\log$ function in Eq. \ref{eq_motions} has been regularized by adding a unity constant \citep{Chester2007}.

The LES algorithm has been previously used to study land atmosphere interaction processes \citep{Albertson1999a, Albertson1999} and to develop and test linear and non-linear LES subgrid-scale models \citep{Meneveau1996a, Porte-Agel2000, Port2004, Bou-Zeid2005, Lu2010, Lu2013}.

Equations are solved in strong form on a regular domain $\Omega$, a pseudo-spectral collocation approach \citep{Orszag1969a, Orszag1970} based on truncated Fourier expansions is used in the $x,y$ coordinate directions, whereas a second-order accurate centered finite differences scheme is adopted in the vertical direction, requiring a staggered grid approach for the $\tilde{u},\tilde{v},\tilde{p}$ state variables (these are stored at $(j+1/2)dz$, with $j=1,nz$).
Time integration is performed adopting a fully explicit second-order accurate Adams-Bashforth scheme and a fractional step method \citep{Alexandre1968, Fluid1985} is adopted to compute the pressure field, which is based on an operator-splitting technique.
In addition, nonlinear terms are deliased via the $3/2$ rule \citep{Canuto2006}, to avoid piling up of energy in the high wavenumber range \citep{Kravchenko1997a}.
The computational boundary is partitioned as $\partial \Omega = \Gamma_{\mathrm{b}} \cup \Gamma_{\mathrm{top}} \cup \Gamma_{lateral}$, where $\Gamma_{\mathrm{top}}$ and $\Gamma_{lateral}$ denote the top and lateral boundaries respectively. A free-lid boundary condition applies at $\Gamma_{\mathrm{top}}$ and a parameterized boundary condition is prescribed at $\Gamma_{\mathrm{b}}$ (see in Eq. \ref{eq_motions}). 
Periodic boundary conditions apply at $\Gamma_{lateral}$ due to the Fourier spatial representation.

\subsubsection{Subgrid-scale closure model}
The proposed study considers two LES closure models to evaluate $\tau_{ij}^{SGS}$: the classical static Smagorinsky model \citep{Smagorinsky1963} in conjunction with a wall damping function (SMAG), similar to that adopted in \cite{Mason2006}, and the scale-dependent model with Lagrangian averaging of the coefficient (LASD), developed in \cite{Bou-Zeid2005}.

Smagorinsky models rely on the viscous analogy and on the mixing length concept, and evaluate the subgrid-scale terms as a function of the resolved strain rate tensor: 
%
\begin{linenomath*}
\begin{equation}
  \tau_{ij}^{SGS} = - 2 \nu_t \tilde{S}_{ij} = -2  (c_{s,\Delta} \Delta)^2 \| \tilde{S} \|_2 \tilde{S}_{ij} \, ,
    \label{statSmag}
\end{equation}
\end{linenomath*}
%
where $\nu_t$ represents the eddy viscosity, $\Delta$ is the filter width (usually proportional to the grid size), $\tilde{S}_{ij}$ is the filtered shear rate tensor and $c_{s,\Delta}$ is the Smagorinsky coefficient at scale $\Delta$.
The two models essentially differ in the way they compute the Smagorinsky coefficient.

The SMAG model prescribes a constant coefficient, whose value is usually the one derived from the theory of homogeneous turbulence $(c_{s,\Delta}=0.16$, for the sharp spectral cutoff filter).
However, in applications involving high Reynolds number boundary layer flows -- such as the one proposed herein -- the model is known to be over-dissipative in the near wall regions,  where $c_{s,\Delta}$ should approach zero. To cope with this we introduce an empirical wall damping function \citep{Mason2006}, which has the drawback of requiring an ad-hoc calibration for each specific flow case, but partially ameliorates the dissipative properties of the SMAG model.

The LASD model overcomes the necessity of ad hoc specification of the damping function by exploiting the smallest resolved scales to compute the model coefficient at runtime. It represents an evolution of the original dynamic model, based on the Germano identity \citep{Germano1991a} and its modifications \citep{Lilly1992}. 
LASD relaxes the scale invariance assumption of the model coefficient, which is a desirable property in the near wall regions, where the grid size approaches the limits of the inertial subrange \citep{Meneveau2000}.
The Lagrangian averaging of the model coefficient makes the model well suited for applications involving complex geometries, since it preserves local variability while satisfying Galileian invariance, and overcomes the requirement of homogeneous directions \citep{Bou-Zeid2005}. 
Additionally, along fluid pathlines the energy cascade process is more apparent \citep{Meneveau1994}, which enforces the theoretical basis of the model.
To reduce the strong Gibbs oscillations that would arise at the interface if adopting a classic spectral cutoff filter, a Gaussian filter is introduced in conjunction with the LASD model, which has the desirable property of being of compact support in both physical and wavenumber space \citep{Tseng2006}.

\subsubsection{Discrete forcing immersed boundary method (IBM)}

To model the urban canopy a discrete forcing approach immersed boundary method is adopted \citep{Mohd-yusof1997,Mittal2005}. 
The buildings' interface $\Gamma_{b}(x,y)$ is represented implicitly as the zero level-set of a (higher dimensional) signed distance function $\tilde{\phi}(x,y,z)$, and the computational domain $\Omega$ is splitted in two regions: the inside building region $\Omega_b$, where $\tilde{\phi} \leq 0$, and the fluid region $\Omega_f$, where $\tilde{\phi} > 0$.
The $\tilde{\phi}(x,y,z)$ function is initialized adopting an iterative projection technique on the  triangulated (urban) surface, which has been specifically developed for the current study.
The immersed boundary algorithm is a minor modification of the one proposed in \cite{Chester2007}. 
The velocity field is fixed to zero in $\Omega_b$ through a penalty method and the law of the wall is enforced at all the collocation nodes which fall in the region $-1.1 \Delta \le \tilde{\phi} \le 1.1 \Delta$. 
The law of the wall is based on the equilibrium logarithmic assumption \citep{Moeng1984} and computes the local surface stress vector as 
%
\begin{linenomath*}
\begin{equation}
      \mathbf{\tilde{t}} = - \left( \frac{ \kappa ( \mathbf{\tilde{u}} - \mathbf{\tilde{u}}_N )}{\ln{(1+\Delta/z_0)}} \right)^2 \, .
\end{equation}
\end{linenomath*}
%
The main difficulty in coupling the immersed boundary method with a pseudo-spectral algorithm is represented by the fact that the domain is not simply connected. 
The solution to Eqs. \ref{eq_motions}, in a given plane cutting the building elements, is of class $C^0$, with the discontinuities in first derivatives localized at the building-atmosphere interface $\Gamma_{b}$. The spectral representation will result in Gibbs oscillations in the near interface regions, which will then propagate away from the singularity and degrade the quality of the partial sum approximation \citep{Geer1997}.
To alleviate such phenomena a smooth velocity profile $\tilde{u}_i$ is generated in $\Omega_b$ ($\tilde{\phi} \le 0$) before the spectral differentiation step \citep{Tseng2006} adopting a Laplacian smoothing operator which resembles the reconstruction scheme proposed in \citet{Cai1989} and \citet{Geer1997}. 
Alternative smoothing algorithms are also available, as in \citet{Fang2011} and \citet{Li2016}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Site description and instrumentation}

Numerical solutions are compared to field data from the Basel Urban Boundary Layer Experiment (BUBBLE), a multi-institutional effort dedicated to the energetics and dispersion processes in the urban boundary layer \citep{Rotach2005}.
%
\begin{figure}[h]
	\centering
%	\begin{tabular}{c c}
      		\includegraphics[width= 120.0mm]{./reference_surface_contour} 
%        \end{tabular}
     	\caption{\label{basel1} Color contour of the surface height $(\Gamma_{\mathrm{b}}(x,y))$ for a neighborhood scale of $512\times512 \ \mathrm{m}$, centered at the tower location. The Sperrstrasse street canyon is aligned with the $x$ coordinate axis.}
\end{figure}

%		\includegraphics[width= 25.0mm]{images/tower_picture}

%
During BUBBLE, a $32 \ \mathrm{m}$ high tower was deployed inside the $13 \ \mathrm{m}$ wide Sperrstrasse street canyon in Basel, Switzerland $(47^{\circ}33'57.20"\mathrm{N}, 7^{\circ}35'48.80"\mathrm{E}, \mathrm{WGS}-84)$, as displayed in Fig. \ref{basel1}. 
The orientation of the street canyon is along the axis $066^{\circ} - 246^{\circ}$ (ENE to WSW), the block where the tower was operated is characterized by a length of $160 \ \mathrm{m}$, and an average width-to-height ratio of $\xi_c / z_h = 1.0$, where $\xi_c$ is the street canyon width and where $z_h$ is the mean building height. 
%
\ctable[cap = {Details on the tower instrumentation},
           caption = {Details on the ultrasonic anemometer-thermometer (sonic) instrumentation, label, absolute measurement heights $z$, normalized measurement heights (the normalization scale is the location of the highest sonic), sonic type, sampling frequency $f \ (\mathrm{Hz})$.},
            label={sonicTable},
            doinside=\small \renewcommand\arraystretch{1.2},
            pos = ht,
            width   = 110mm,]{>{\hsize=.5\hsize}X >{\hsize=.5\hsize}X >{\hsize=.5\hsize}X >{\hsize=1.2\hsize}X >{\hsize=.5\hsize}X}
{
  % You specify table footnotes here.
}{
\FL % FLORIDA (just kidding, means "first line")s
    Label & $z \ (\mathrm{m})$ & $z/z_t$ & Instrument type & $f \ (\mathrm{hz})$ 		\ML % middle line
    %
    $A$ & 3.6 & 0.11 & Gill R2 Omnidirectional & 20.8  			\\
    %
    $B$ & 11.3 & 0.35 & Gill R2 Omnidirectional & 20.8 			\\
    %
    $C$ & 14.7 & 0.46 & Gill R2 Omnidirectional & 20.8			\\
    %
    $D$ & 17.9 & 0.56 & Gill R2 Omnidirectional & 20.8			\\
    %
    $E$ & 22.4 & 0.7 & Gill R2 Asymmetric & 20.8				\\
    % 
    $F$ & 31.7 & 1 & Gill HS & 20.0                              			\LL 
}
%
The tower was placed at the midpoint of the block, $3 \ \mathrm{m}$ away from the north wall, and equipped with six ultrasonic anemometer-thermometers (sonics, labels $A-F$ in table \ref{sonicTable}), mounted on horizontal booms reaching from the tower into the centre of the street canyon.

%
% SITE DESCRIPTION
%
Buildings on both sides of the street canyon ``Sperrstrasse" have pitched roofs except two
flat-roof buildings directly adjacent to the tower on the northern side (label 1 and 2 in Fig. \ref{basel1}) and two flat-roof buildings close to the two intersections (label 3 and 4). The height of buildings typically reaches $15 \ \mathrm{m}$ on both sides. A high pitched roof of $20 \ \mathrm{m}$ is located directly to the south-east of the tower (label 5) \citep{Christen2009}.
Sectors from west to NNE and SSE to SSW are similar to structures found immediately around the tower.
These sectors are homogeneous in terms of integral morphometric statistics and building height with fetch extending to $700 \ \mathrm{m}$. In the sector NE to SSE an extensive commercial area is found at $100 \ \mathrm{m}$ distance to the tower with flat roofs and roof heights from $20 \ \mathrm{m}$ to $25 \ \mathrm{m}$ (label 6), whereas an isolated high-rise building of $64 \ \mathrm{m}$ height is located $\approx 200 \ \mathrm{m}$ to the south-west of the tower (label 7). 
A $18.5 \ \mathrm{m}$ building is located approximately $100 \ \mathrm{m}$ north-east of the tower (label 8).
For the considered neighborhood, trees are all of the same height and lower than buildings, and the plan area fraction of vegetation (grass plus trees) is only 0.16 \citep{Christen2004}.

\subsection{The urban canopy dataset}
A high resolution three dimensional terrain and building digital model (vector format) which includes downtown and sub-urban areas of Basel, was provided by the authorities of the city (GVA Grundbuch und Vermessungsamt Basel-Stadt). 
The building model includes details such as openings and chimneys, but does not include vegetation. Neglecting vegetation is justified considering its small plan area fraction (0.16).
The dataset was rasterized at a horizontal resolution of $0.5 \ \mathrm{m}$ and rotated by $-24^{\circ} (\text{clockwise})$ in order to have the main street canyon aligned with the coordinate system $(x,y,z)$, as in Fig. \ref{basel1}. 
The pdf of roof heights is characterized by a trimodal distribution (see left plot in Fig. \ref{roofs_stats}) with modes at $z \approx 4.5 \ \mathrm{m}$ (Mo$_1$), $z \approx 17.5 \ \mathrm{m}$ (Mo$_2$) and $z \approx 22.5 \ \mathrm{m}$ (Mo$_3$).
The mean roof height $z_h$ is $15.3 \ \mathrm{m}$ and the variance of roof height is $6.4 \ \mathrm{m}$. 
The first mode Mo$_1$ corresponds to one-storey buildings in the backyards (garages, commercial buildings, etc.), the second mode Mo$_2$ is related to the the main residential (attached) buildings that line streets and enclose courtyards, whereas the third mode Mo$_3$ is linked to building N.6 in Fig. \ref{basel1}, whose large surface has significant impact on the pdf of the surface heights.
%
\begin{figure}
	\centering
        \begin{tabular}{c c}
        \includegraphics[width= 75.0mm]{./histo_roofs} &
        \includegraphics[width= 30.0mm]{./plan_area_fraction} 
       \end{tabular}
       \caption{Binned pdf of the roof heights (left) and plan area fraction $\lambda_p(z)$ (right) for the considered surface ($512 \times 512 \ \mathrm{m}$). }
      \label{roofs_stats}
\end{figure}
%

\subsection{Processing of the profile tower dataset}

Wind components $u,v,w$ and virtual acoustic temperature $\theta$ were continuously recorded at all six levels simultaneously from December 1, 2001 to July 15, 2002.
Data acquisition systems and quality control procedures including wind-tunnel calibrations of the instruments are described and documented in \cite{Christen2005}.
$u,v$ and $w$ statistical moments up to order three were calculated and stored for blocks over 5 minutes. No filtering was applied to the signal nor standard de-trending, to ensure energy conservation and enable vertical gradients of the state variables to be properly computed. 
To provide data for comparison with pressure driven simulations the following processing is further performed:
%
\begin{enumerate}
	\item data are averaged in blocks of 30 minutes;
	\item data are selectively sampled from the year-round dataset based on the wind direction computed at the tower top sensor. Only $30$ min blocks characterized by an approaching wind direction of $\alpha =  66^{\circ} \pm 10^{\circ}$ (along-canyon regime) and of $\alpha = 156^{\circ} \pm 10^{\circ}$ (across-canyon regime) throughout the $6 \times 5$ min intervals are kept;
	\item in order to eliminate the influence of thermal stability, the periods are further filtered based on the classic stability parameter $\zeta = (z - z_d)/L$ \citep{Stull1988}, where $L$ is the Obukhov length $(L = \theta u^2_{\tau} / [\kappa g \theta_*])$ calculated with both friction velocity $u_{\tau}$ and scaling temperature $\theta_*$ measured at the tower top. Only periods characterized by near-neutral stability are kept, $-0.1 \le \zeta \le +0.1$. The displacement height is computed as $z_d=2/3 z_h$, in the typical range suggested for high-density urban roughness elements \citep{Grimmond1999};
	\item cases characterized by $u_{\tau} \le 0.15 \ \mathrm{ms^{-1}}$ at tower top are excluded from the analysis.
\end{enumerate}
%
Despite the strict constraints, the availability of a relatively long dataset resulted in $30$ blocks for the ENE wind approaching direction ($\alpha =  66^{\circ} \pm 10^{\circ}$) and $3$ blocks for the SSE wind approaching direction ($\alpha =  156^{\circ} \pm 10^{\circ}$).

\subsection{Setup of simulations}

%
\ctable[cap = {Geometrical and numerical parameters for the LES runs. },
           caption = {Geometrical and numerical parameters for the LES runs.},
            label={domainSizeParam},
            doinside=\small \renewcommand\arraystretch{1.0},
            pos = ht,
            width   = 100mm,]{>{\hsize=.25\hsize}X >{\hsize=.25\hsize}X >{\hsize=.25 \hsize}X >{\hsize=.25 \hsize}X}
{
  % You specify table footnotes here.
  \tnote[]{}
}{
\FL % FLORIDA (just kidding, means "first line")
     ID & $ z_0 \ \mathrm{(m)}$ & $\alpha$ (deg) & SGS model \ML   %
    $A$ &  $\Delta/15$ & $66$ & SMAG \\
    $B$ & $\Delta/30$ & $66$  & SMAG   \\
    $C$ &  $\Delta/15$ & $156$  & SMAG \\
    $D$ & $\Delta/30$ & $156$ & SMAG   \\
    $E$ &  $\Delta/15$  & $66$& LASD \\
    $F$ &  $\Delta/30$ & $66$  & LASD   \\
    $G$ &   $\Delta/15$ & $156$  & LASD \\
    $H$ &  $\Delta/30$ & $156$ & LASD   \LL
    }
	Simulations are performed over a regular domain, of size $L_x \times L_y \times L_z = 512 \times 512 \times 160$, (horizontally) centered at the tower locations $(x_t,y_t)$ and discretized with $1 \, \mathrm{m}$ stencil in the three coordinate directions ($x,y,z$). 	
	Numerical parameters for each run are summarized in Table \ref{domainSizeParam}. 
	Two directions of the incoming wind are considered, $\alpha = 66^{\circ}$ and $\alpha = 156^{\circ}$, which correspond to an along-canyon and across-canyon wind regime respectively. 
	The flow is forced by imposing a constant pressure gradient $\partial_x p_{\infty} /\rho$, which, in conjunction to lateral periodic boundary conditions, defines a friction velocity $u_{\tau} = \sqrt{(\delta-z_d)\partial_x p_{\infty}/\rho}  \approx 1.23 \ \mathrm{m \ s\textsuperscript{-1}}$, making the system independent from Reynolds number effects (fully rough flow regime). 
	Under such conditions it is possible to scale the solution throughout the boundary layer with a characteristic velocity $U$, since molecular diffusion is negligible.
	The relatively homogeneous integral morphometric statistics and buildings height in the neighborhood justifies the pressure forcing in conjunction with lateral periodic boundary conditions  (the main surface transition occurs at $\approx 700 \ \mathrm{m}$ in the radial direction from the tower location).	Domain size was chosen based on a sensitivity study (not shown).
%, adopting Wood's equation for the growth of the internal boundary layer (IBL) \cite{Wood1982a}
%%
%\begin{equation}
%     z_{H}^{IBL}/k_{or} = 0.28 \left(  x_i/k_{0r} \right)^{0.8},
%\end{equation}
%%
%where $z_{H}^{IBL}$ is the height of the IBL, $x_i$ is the stream-wise coordinate direction and $k_{0r}$ is the larger of the surface roughnesses $k_{01}, k_{02}$ characterizing the transition, would result in $\partial z_{H}^{IBL}/ \partial x_i \approx 0.05m/m$ and $\langle z_{H}^{IBL} \rangle=50m$. The growth of the IBL is therefore a minor percentage of the average $z_{H}$ in the domain of interest and justifies the approach.
	The hydrodynamic roughness length $z_0$, defining the surface roughness, is not known a priori. Here, $z_0$ is defined based on a Nyquist-Shannon representation criteria \citep{Shannon1949}: adopting a reference grid stencil $\Delta$, the smallest flow/surface feature that is representable through the Fourier partial sums is $k_{\Delta} = 2\Delta$, whereas all scales smaller than $k_{\Delta}$ need to be modeled. 
	Since $z_0 = 0.033 k_s$, where $k_s$ is the equivalent Nikuradse sand grain roughness, and given that $k_s \rightarrow k$ in the limit of negligible viscous effects ($k$ is the height of the considered roughness element), we have that $z_0 = 0.033 k_{\Delta} \approx \Delta/15$. 
	To account for variations in the solution due to the $z_0$ parameter $z_0= \Delta / 30$ is also considered.
	To reduce the computational time required to reach a dynamic equilibrium, the initial velocity field for each simulation is imposed through interpolation from results of a run at coarser resolution (twice as coarse in each coordinate direction). 
	Equations are integrated in time for $480$ non-dimensional time units $T = z_h/u_{\tau}$ ( $\approx 2 \ \mathrm{hours}$ in dimensional time) in the coarser grid, before being used as initial condition for the finer grid, where they are further integrated for $250T$. 
$100T$ are required in order to achieve statistical stationarity in the velocity field and $150T$ are used to compute statistics, which ensures convergence of first and second order moments to the corresponding expected values.
	To further reduce computational costs the $\delta/z_h \gtrapprox 50$ requirement \citep{Jimenez2004} is here sacrificed. Simulations are characterized by $\delta/z_h = 10.6$. Roughness has a great influence on turbulence up to ${z/z_h \approx \min(1+D/z_h,5)}$, where $D$ is the separation distance between nearest-neighbour roughness elements \citep{Raupach1981, Jimenez2004}. Assuming the top of the RSL to be located at $z/z_h=5$ implies that the current geometry does not allow an ISL to survive. 
	The limited $\delta /z_h$ in the proposed study might be justified by considering that the focus is on the dynamics within the RSL.
In these regions turbulence is expected to be strongly affected by the morphology of the roughness elements and only in minor part by dynamics of the logarithmic and outer layer \citep{Anderson2016a}.

### 2016-06-23 paper_BLM.tex
pre-review

--- 2015-10-16 paper_BLM.tex
@@
 % proceed on the \documentclass line
-% your LaTeX will extract the file if required
+%% your LaTeX will extract the file if required
 \begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-%
+%%!PS-Adobe-3.0 EPSF-3.0
+%%%BoundingBox: 19 19 221 221
+%%%CreationDate: Mon Sep 29 1997
+%%%Creator: programmed by hand (K)
+%%%EndComments
+%%
 gsave
@@
 %
-%\documentclass{svjour3}                     % onecolumn (standard format)
+\documentclass{svjour3}                     % onecolumn (standard format)
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %\documentclass[twocolumn]{svjour3}          % twocolumn
-%
+%\documentclass[referee]{svjour3} 
 \smartqed  % flush right qed marks, e.g. at end of proof
@@
 \usepackage{color}
-\usepackage{ctable}
+%\usepackage{ctable}
 %\usepackage{epsfig}
-\usepackage{hyperref}
-\usepackage{soul}
-\usepackage{amssymb}
+%\usepackage{hyperref}
+%\usepackage{soul}
+%\usepackage{amssymb}
 % etc.
@@
 % Insert the name of "your journal" with
- \journalname{Boundary-Layer Meteorology}
+ \journalname{Boundary-Layer Meteorology Research Note}
 
@@
 
-\title{Exact analytic solution for slope flows with spatially varying eddy viscosity and diffusivity}
+\title{On the solution of katabatic flows with spatially varying eddy viscosity and diffusivity}
 
@@
 %\authorrunning{Short form of author list} % if too long for running head
-\author{M.~G.~Giometto \and R.~Grandi\and J.~Fang \and M.B. Parlange}
+\author{M.~G.~Giometto \and R.~Grandi\and J.~Fang \and M.~B.~Parlange}
 
-\institute{ M.G. Giometto \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
+\institute{ M.~G.~Giometto \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
 		\email{marco.giometto@epfl.ch}
 		\and
-		Riccardo Grandi \at Mathematics Institute for Geometry and Applications, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
+		R.~Grandi \at Mathematics Institute for Geometry and Applications, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
 		 \and 
-		 J. Fang \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
+		 J.~Fang \at School of Architecture, Civil and Environmental Engineering, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
 		 \and
-		M.B. Parlange \at Civil Engineering, Faculty of Applied Sciences, University of British Columbia, Vancouver, BC, Canada
+		M.~B.~Parlange \at Dept. of Civil Engineering, Faculty of Applied Science, University of British Columbia, Vancouver, BC, Canada
 }
@@
 \begin{abstract}
-An exact analytic solution of the steady-state Prandtl model equations is derived, valid for spatially varying eddy diffusivities (O'Briens type) and Prandtl number of unity. 
-In this formulation profiles show significant variations in both phase and amplitude of minima-maxima with respect to the classic constant eddy viscosity model and the more recent, approximate, WKB solution.
-The near wall region is characterized by a relatively stronger surface inversion and velocity gradients, the low-level-jet is further displaced toward the wall, and its peak velocity strongly depends on the model parameter, suggesting a tighter coupling between dynamics and thermodynamics.
+The Nieuwstadt closed form solution for the stationary Ekman layer is generalized for katabatic flows within the conceptual framework of the Prandtl model. 
+The solution is valid for spatially-varying eddy viscosity and diffusivity (O'Brien type) and constant Prandtl number $(Pr)$. 
+Momentum and buoyancy transfer coefficients are specified in accordance with Monin-Obukhov similarity.
+The characteristics of the solution are discussed as a function of the dimensionless model parameters $Pr$ and $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$, where $\hat{z}_0$ is the hydrodynamic roughness length, $\hat{b}_s$ is the imposed surface buoyancy and $\hat{N}$ is the Brunt-V\"ais\"al\"a frequency.
+For the considered range of such parameters, velocity and buoyancy profiles show significant variations in both phase and amplitude of extrema with respect to the classic constant-$K$ model and a more recent approximate solution based on the Wentzel-Kramers-Brillouin (WKB) theory.
+Near-wall regions are characterized by relatively stronger surface momentum and buoyancy gradients, whose magnitude is inversely proportional to $Pr$.
+In addition, slope-parallel momentum and buoyancy fluxes are reduced, the low-level jet (LLJ) is further displaced toward the wall, and its peak velocity strongly depends on $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$.
+
+%Simple approximate functions (based on the new solution) are provided, to relate the internal parameters of the system $(u_*, b_*)$ to the given external parameters.
+%Universal functions are also provided to describe the variation of $ z_j$, $z_r$, and $\max{(u)}$, as a function of the dimensionless model parameter $z_0$.
 \end{abstract}
@@
 \section{Introduction}
-Natural convection of turbulent stratified flows over sloping surfaces is ubiquitous in nature and engineering, and is of interest not only as a fundamental problem in itself, but also because of the important role it plays over a broad range of scales and applications.
-On a local scale, for instance, it governs local weather conditions, affecting atmospheric transport processes and dispersion of scalars such as heat and humidity \citep{Monti2002, Nylen2004b}. 
-On a regional scale, it drives the development of deep-convective circulations \citep{Egger1985, Parish1998} and is responsible for intense cyclonic vorticity in the middle and upper troposphere \citep{Parish1992}.
-Further, recent experimental field campaigns \citep{Chu1987, Oerlemans1993} have shown that persistent katabatic winds characterize the atmospheric boundary layer over snow-ice surfaces and glaciers, and therefore an accurate characterization of such flows is an essential component of understanding and modeling of the weather and climate.
-However, the complex dynamics (e.g.
-occurrence of intermittency, waves, Kelvin-Helmholtz instabilities and low-level jets) and the lack of a satisfactory similarity theory for such flows \citep{Nadeau2012} pose a heavy burden in terms of computational requirements for numerical modellers; in most cases the required resolution is prohibitively costly \citep{Shapiro2004, Shapiro2004a, Fedorovich2009, Fedorovich2009d, Burkholder2011a}.
+Slope winds are ubiquitous in nature and engineering, and they are of interest not only as a fundamental problem in itself, but also because of the important role they play over a broad range of scales and applications.
+On a local scale, for instance, they regulate local weather conditions, influencing atmospheric transport of momentum and scalars such as heat and humidity \citep{whiteman1990, Whiteman, Monti2002, Nylen2004b, Rotach2007, Lehner2015}.
+On a regional scale, they can be responsible for intense cyclonic vorticity in the middle and upper troposphere \citep{Parish1991, Parish1992, Parish1998}.
+Persistent katabatic winds characterize the atmospheric boundary layer over Antarctica \citep{Chu1987, Renfrew2004, Renfrew2006a} and over glaciers \citep{Oerlemans1993, Oerlemans1994, pastex1994, Greuell1997, Smeets1997, Oerlemans1998, oerlemans1999, Smeets2000, Oerlemans2002}.
+Therefore an accurate characterization of such flows is an essential component of understanding and modeling of the weather and climate.
+The problematic geometrical setup complicates measurements \citep{Oldroyd2015}, whereas the complex dynamics (e.g.
+turbulent intermittency, waves, Kelvin-Helmholtz instabilities, low-level jets) and the lack of a satisfactory similarity theory for such flows \citep{Nadeau2012} pose a challenge in terms of computational requirements for numerical modelers.
+In most cases the required resolution is in fact prohibitively costly \citep{Fedorovich2009, Fedorovich2009d, burkholder_2011}.
 Because of this, conceptual models are still of great interest, and represent a valid tool for the characterization of such systems.
-A cornerstone in the understanding of natural convection of stratified fluid along a sloping surface is represented by the classic Prandtl analytic model \citep{Prandtl}, and its more recent extensions/generalizations to include the effects of Coriolis force \citep{Gutman1964}, external winds \citep{Lykosov_1972}, surface heterogeneity \citep{Egger1985, Shapiro2007, Oldroyd2014}.
-The Prandtl model approximates the atmosphere in a Boussinesq sense and describes a steady flow over a thermally perturbed unbounded planar sloping surface that lies within a stratified environment, given by the following system of equations:
-%
-\begin{linenomath*}
-\begin{eqnarray}
-	N^2 u(z) \sin{\alpha} & = & d( K_H db/dz )/dz,
-	\label{eqn1u} \\
-	%
-	b(z) \sin{\alpha} & = & -d( K_M du/dz )/dz,
-	\label{eqn1b}
-\end{eqnarray}
-\end{linenomath*}
-%
-where $z$ denotes the normal-to-slope coordinate directions, $u$ is the downslope velocity, $b$ is buoyancy, $N$ is the buoyancy frequency characterizing the system (related to the background stratification), $\alpha$ is the slope angle and $K_M$ and $K_H$ denote the eddy viscosity and diffusivity (an eddy viscosity/diffusivity model has been used to parametrize turbulent fluxes of momentum and buoyancy).
-Equations are integrated in $z \in \ [0,H]$ with boundary conditions $u(0)=0$, $u(H) = 0$, $b(0)=b_s$ and $b(H) = 0$ ($b_s > 0$ for upslope flows, whereas $b_s<0$ for downslope flows).
 
-The flow is assumed to be invariant in the downslope direction and the model can be used to determine its vertical structure \citep{NAPPO1987}.
-Eqs.
-\ref{eqn1u} and \ref{eqn1b} state that downslope (upslope) convection of cold (warm) air is balanced by momentum flux divergence, and that along-slope generated buoyancy is balanced by buoyancy flux divergence; thus the model is applicable away from ridges and valleys, so that advection terms are negligible \citep{NAPPO1987}.
-The Prandtl constant-K model is known to be overdissipative in the near surface regions, and therefore not able to represent the observed strong surface gradients of temperature and momentum that commonly characterize katabatic and anabatic flows \citep{Oerlemans1998, grisogono2001katabatic}.
-Simple variations in the eddy diffusivity profiles were introduced in an exact analytic solution by \citet{gutman_1983}, and more recently \citet{grisogono2001katabatic} considered general variations in the vertical structure of the eddy diffusivities, and derived  solutions based on the WKB approximation.
-The WKB solution is able to account for additional dynamics while still retaining an elegant form.
-However, that theory is only applicable when the model parameters $(K_M, K_H)$ vary more slowly than the solution $(u,b)$, and the validity of such a constraint for slope flows has been the subject of great debate \citep{Grisogono2002}.
-In the following, we derive a closed-form solution to the Prandtl-model equations, valid for O'Brien's type \citep{O'Brien1970} eddy diffusivities and representing an exact alternative to the WKB solution -- for the chosen form of the model parameter.
-
-% ###################################################################
-\section{The Analytic Solution}
-%
-We consider the one-dimensional Prandtl model equations \ref{eqn1u} and \ref{eqn1b}.
-Assuming $Pr=1$ (i.e.
-$K_M=K_H=K$) and assigning length, velocity and buoyancy scales as $L=\max{(K)}^{1/2} N^{-1/2} \sin^{-1/2}{\alpha}$, $U=b_s N^{-1}$ and $B=b_s$ Eqs.
-\ref{eqn1u} and \ref{eqn1b} can be reduced to:
+A cornerstone in the understanding of slope flows is represented by the classic Prandtl analytic model \citep{Prandtl}, afterwards extended to include Coriolis force \citep{Gutman1964}, external winds \citep{Lykosov_1972}, and surface variability \citep{Shapiro2007, Oldroyd2014,Zardi2015}, to name but a few.
+The Prandtl model approximates the atmosphere in a Boussinesq sense and describes a steady stratified flow over a thermally perturbed unbounded planar sloping surface.
+It is summarized by the following system of ordinary differential equations:
 %
@@
 \begin{subequations}
-\label{ode}
 	\begin{align}
-	u^+& = d( K^+ db^+/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
-	\label{eqn1u_norm} \\
+	- \hat{N}^2 \hat{u}(\hat{z}) \sin{\alpha} & = [ \hat{K}_H \hat{b}_{\hat{z}} ]_{\hat{z}} \, , \\
+	\hat{b}(\hat{z}) \sin{\alpha} & = [ \hat{K}_M \hat{u}_{\hat{z}} ]_{\hat{z}} \, ,
+	\end{align}
+	\label{Prandtl_eq}
+\end{subequations}
+\end{linenomath*}
 %
-	b^+ & = -d( K^+ du^+/dz^+ )/dz^+, &&\mathrm{in}  \ [0,H^+]
-	\label{eqn1b_norm}
+where $\hat{(\cdot)}$ is used to denote a dimensional variable or parameter, $(\cdot)_{\hat{z}}$ denotes differentiation with respect to the slope-normal coordinate direction $\hat{z}$, $\hat{u}$ is the downslope velocity, $\hat{b} \equiv \hat{g} \hat{\theta}^{\prime} / \hat{\theta}_0$ is buoyancy, where $\hat{g}$ is the gravitational acceleration, $\hat{\theta}^{\prime}$ is the potential temperature perturbation (with respect to the background stably stratified environment characterized by the Brunt-V\"ais\"al\"a frequency $\hat{N}$), and $\hat{\theta}_0$ is a reference (constant) temperature; $\alpha$ is the slope angle and $\hat{K}_M$ and $\hat{K}_H$ denote the eddy viscosity and diffusivity (a model is used to parametrize turbulent fluxes of momentum and buoyancy, respectively).
+Equations are defined in $\hat{z} \in \ [\hat{z}_0,\infty)$ with boundary conditions $\hat{u}(\hat{z}_0)=0$, $\hat{u}(\hat{z} \rightarrow \infty) = 0$, $\hat{b}(\hat{z}_0)=\hat{b}_s$ and $\hat{b}(\hat{z} \rightarrow \infty) = 0$ ($\hat{b}_s > 0$ for upslope flows, whereas $\hat{b}_s<0$ for downslope flows).
+Eqs. 1 state that the slope-parallel component of buoyancy is balanced by momentum flux divergence, and that slope-parallel buoyancy advection is balanced by buoyancy flux divergence.
+The flow is assumed to be invariant in the along-slope direction and the model can be used to determine the slope-normal $(\hat{z})$ structure of velocity $\hat{u}(\hat{z})$ and buoyancy $\hat{b}(\hat{z})$.
+The model is applicable far enough away from ridges and valleys that non-linear advection terms become small \citep{NAPPO1987}, and a balance between advection and diffusion (of both momentum and buoyancy) is achieved.
+This constraint is rather restrictive, as shown in \citet{Zardi2015}.
+The Prandtl constant-K solution reads 
+%
+\begin{linenomath*}
+\begin{subequations}
+	\label{Prandtl_sol}
+	\begin{align}
+		\hat{b} & = \hat{b}_s \exp{(-\hat{\sigma}_c \hat{z})} \cos{(\hat{\sigma}_c \hat{z})} \, , \\
+		\hat{u} & = -\frac{\hat{b}_s}{N Pr} \exp{(-\hat{\sigma}_c \hat{z})} \sin{(\hat{\sigma}_c \hat{z})} \, ,
 	\end{align}
@@
 %
-respectively, where $K^+$ is a normalized eddy viscosity, $z^+=zL^{-1}$, $u^+ = uU^{-1}$, $b^+=b B^{-1}$, with boundary conditions $u^+(0)=0$, $u^+(H^+) = 0$, $b^+(0)=\pm 1$ and $b^+(H^+) = 0$.
+where
 %
-Further, we introduce the following variables 
+\begin{eqnarray}
+	\hat{\sigma}_c^2 \equiv \frac{\hat{\sigma_0}}{2\hat{K_H}} \, , \qquad \mathrm{and} \qquad
+	\hat{\sigma}_0 \equiv \frac{\hat{N} \sin{(\alpha)}}{\sqrt{Pr}} \, .
+\end{eqnarray}
+%
+The model is able to represent the low-level jet (LLJ) and the return flow region, key features of observed katabatic and anabatic flows. 
+However, the constant-K solution is also known to be over-dissipative in the near-surface regions, and under dissipative above the LLJ regions \citep{Defant1949,Oerlemans1998, grisogono2001katabatic}.
+It is therefore not able to represent the observed strong surface gradients of temperature and momentum, and, in addition, the predicted wind speed typically decreases too rapidly away from the surface.
+Simple variations in the eddy diffusivity profiles were introduced in a patched analytic solution by \citet{gutman_1983}, whereas more recently \citet{grisogono2001katabatic} considered general variations in the vertical structure of the eddy diffusivities, and derived  a patched global solution based on the WKB approximation \citep{Bender1979}.
+The WKB solution to the Prandtl equations, valid to leading-order in the inner layer and to first-order in the outer layer, reads
+%
+\begin{subequations}
+	\begin{align}
+		\hat{f}_{in} & \sim  \exp{ \left( -(1 \pm i) (\hat{\sigma}_0/2)^{1/2} \int_0^{\hat{z}}{\hat{K}_H(z)^{-1/2}}{\mathrm{d}z}\right)}  &  \hat{z} \in [\hat{z}_0,\hat{h}] \, , \\
+		\hat{f}_{out}&  \sim  [ \hat{K}_H(\hat{z}) / \hat{K}_H(\hat{h}) ]^{-1/4} \exp{ \left( -(1 \pm i) (\hat{\sigma}_0/2)^{1/2} \int_0^{\hat{z}}{\hat{K}_H(z)^{-1/2}}{\mathrm{d}z} \right)} & \hat{z} \in [\hat{h},\infty) \, ,
+	\end{align}
+	\label{WKB_sol}
+\end{subequations}
+%
+where $\hat{f}_{in} \equiv \hat{b}_{in}+ i\hat{u}_{in}$ represents the inner-layer solution, and $\hat{f}_{out} \equiv \hat{b}_{out} + i\hat{u}_{out}$ is the outer-layer solution.
+$\hat{f}_{in}$ and $\hat{f}_{out}$ are patched at $\hat{z}=\hat{h}$, which separates the inner from the outer layer.
+The WKB solution is able to account for additional dynamics while still retaining an elegant form.
+However, WKB theory is only applicable when the model parameters $(\hat{K}_M,\hat{K}_H)$ vary more slowly than the solution $(\hat{u},\hat{b})$, and the validity of such a constraint for slope flows has been the subject of debate \citep{Grisogono2002}.
+
+Here, a closed-form solution to the Prandtl-model equations is derived on a finite domain ($\hat{z} \in [\hat{z}_0,\hat{H}]$), valid for eddy viscosity and diffusivity coefficients that are modeled as a limited range of cubic polynomials, similar to what was proposed in \citet{O'Brien1970} for the planetary boundary layer.
+The derivation is a generalization of the solution proposed in \citet{Nieuwstadt1983a}, where the Ekman-layer equations were solved for the same form of momentum transfer coefficient.
+Recall that the Ekman-layer equations can be reduced to the Prandtl equations after simple changes of variables \citep{Veronis1970}. 
+The solution, expressed as a combination of Gaussian hypergeometric functions, represents an exact alternative to the WKB formulation for the chosen form of the eddy diffusivities. 
+Its sensitivity to variations in the parameter space are investigated here within the Monin-Obukhov framework, to provide insight on the coupling between the velocity and buoyancy fields.
+
+%sloping angle $\alpha \, \mathrm{(deg)}$ and hydrodynamic roughness length $z_0 \, \mathrm{(m)}$ parameters.
+
+% ####################################################################
+\section{Specification of $\hat{K}(\hat{z}$)}
+
+%The characteristics of $\hat{K}(\hat{z})$ in katabatic flows were thoroughly justified in \citet{Grisogono2002}, whom outlined the following criteria that $\hat{K}(\hat{z})$ should honor:
+%%
+%\begin{enumerate}
+%\item realizability condition: $\hat{K}(\hat{z}) \ge 0$;
+%\item $\hat{K}(\hat{z}_0 < \hat{z} \ll \infty) = 0$;
+%\item $\max(\hat{K}(\hat{z}))$, reached at $\hat{z}=\hat{h}$, must lie within the dynamic and thermal boundary layers;
+%\item $\hat{h} > \max(2 \hat{z}_j, \hat{z}_{inv})$;
+%\end{enumerate}
+%%
+%where $\hat{z}_j$ is the height of the LLJ, and $\hat{z}_{inv}$ is the height of the surface inversion layer (in general we have $\hat{z}_{inv} > \hat{z}_j$).
+
+Here, eddy diffusivities are prescribed in line with the classic O'Brien's model \citep{O'Brien1970}, viz. 
+%
+\begin{equation}
+	\hat{K}(\hat{z}) = \kappa \hat{u}_*\hat{z}(1-\hat{z}/\hat{H})^2  \qquad \hat{z} \in [\hat{z}_0,\hat{H}] \, ,
+\end{equation}
+%
+where $\kappa$ is the von K\'arm\'an constant, $\hat{u}_* = \kappa (\hat{z} \hat{u}_{\hat{z}})|_{\hat{z}_0}$ is the friction-velocity, and $\hat{H}$ is the height of the domain, controlling both shape and magnitude of $\hat{K}$.
+The O'Brien model complies with the $\hat{K}$-requirements defined in \citet{Grisogono2002}, and has often been used in studies of stable boundary layers (see for instance \citet{pielke1984mesoscale} and \citet{Stull1988}).
+A generalized O'Brien model was also recently adopted in \citet{grisogono2001katabatic} to study katabatic flows.
+In the original O'Brien's formulation $\hat{H}$ corresponds to the boundary layer depth; in this study $\hat{H}=3\hat{h}$ is evaluated iteratively under the constraint $\hat{h}=\hat{z}_r$, where $\hat{z}_r$ is the height of the peak velocity magnitude in the return flow region.
+Such a choice for $\hat{h}$ is based on a sensitivity analysis that was performed using direct numerical simulations to resolve katabatic flows over steep slopes ($\alpha \geq 15^{\circ}$).
+
+Given the current lack of a rigorous similarity theory for katabatic flows, this study is restricted to the Monin-Obukhov framework, which is expected to yield acceptable approximations of transfer coefficients in the near-surface regions \citep{gutman_1983}.
+Monin-Obukhov similarity is not expected to hold in the above-jet regions, where eddy viscosity and diffusivity coefficients are likely to depend on an additional set of parameters such as the sloping angle $(\alpha)$, the Brunt-V\"ais\"al\"a frequency $(\hat{N})$, and the imposed surface buoyancy $\hat{b}_s$ (or buoyancy flux).
+Nevertheless, the proposed solution is valid in a more general sense, and could easily be adapted in the future to a different $\hat{K}$-parameterisation.
+For instance, one could easily choose a different prefactor than $\kappa$, to make it depend on the model parameters.
+Knowledge of $\hat{u}_*$ and $\hat{H}$ (or equivalently $\hat{h}$) allows one to specify $\hat{K}(\hat{z}) = \kappa \hat{u}_* \hat{z}(1-\hat{z}/\hat{H})^2$.
+
+\section{The Analytic Solution}
+
+For the combination
 %
@@
 \begin{equation}
-   f_1= b^+ - i u^+ \hspace{3mm} \textrm{and} \hspace{3mm} f_2=b^+ + iu^+,
-   \label{combinationVars}
+   \hat{f}= \hat{b} - (i \hat{N} \sqrt{Pr}) \hat{u}
+   \label{combinationVar}
 \end{equation}
@@
 %
-and upon substitution of Eqs.
-\ref{eqn1u_norm} and \ref{eqn1b_norm} into Eqs.
-\ref{combinationVars}, the system can be decoupled to obtain two (independent) complex ordinary differential equations (ODEs) for the canonical variables $f_1$ and $f_2$:
+the system of Eqs. \ref{Prandtl_eq} is reduced to a complex ordinary differential equation (ODE) for the canonical variable $\hat{f}$:
 %
 \begin{linenomath*}
-\begin{subequations}
 \label{ode_norm}
-\begin{align}
-	i \cdot f_1 &=  d(  K^+ df_1/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
-	\label{ode1} \\
-	i \cdot f_2 &= - d( K^+ df_2/dz^+ )/dz^+, && \mathrm{in}  \ [0,H^+]
-	\label{ode2}
-\end{align}
-\end{subequations}
+\begin{equation}
+	\hat{f} = \left[ \frac{-i \hat{K}_M(\hat{z})}{\hat{N} \sin{(\alpha)} \sqrt{Pr}} \hat{f}_{\hat{z}} \right]_{\hat{z}} \qquad \hat{z} \in  \ [\hat{z}_0,\hat{H}] \, ,
+	\label{ode}
+\end{equation}
 \end{linenomath*}
 %
-with boundary conditions $f_i(0)=\pm 1$ and $f_i(H^+) = 0$, $i=1,2$.
-
-We assume eddy diffusivities in line with the classic O'Brien's type \citep{O'Brien1970}, viz. $K^+ = A^+ (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$, where
-$\epsilon^+$ is an additional parameter that we introduce in order to shift the zeroes of $K^+$ outside the interval of integration $[0,H^+]$.
-$\epsilon^+$ can be tuned to provide the desired value of viscosity / diffusivity at the wall.
-
-In order to solve Eqs. \ref{ode1} and \ref{ode2}, we observe that both have the form
+with boundary conditions $\hat{f}(\hat{z}_0)=\hat{b_s}$ and $\hat{f}(\hat{H}) = 0$.
+Assigning a length, velocity and buoyancy scale $\hat{L}= \hat{u}_* \kappa (\hat{N} \sin{\alpha})^{-1}$, $\hat{U}=|\hat{b}_s| \hat{N}^{-1}$ and $\hat{B}=|\hat{b}_s|$ respectively, Eq.
+\ref{ode} reduces to:
 %
 \begin{linenomath*}
-\begin{equation*}
-	f= \mp i \cdot d/dz^+ ( K^+ df/dz^+ ),
-\end{equation*}
+\begin{equation}
+	f =  \frac{-i}{\sqrt{Pr}}\left[ K_M(z) f_z \right]_z \qquad  z \in [z_0,H] \, ,
+	\label{ode_norm}
+\end{equation}
 \end{linenomath*}
 %
-and therefore can be solved using the same method. First, we rewrite the equation in canonical form:
+where $K_M(z) = z(1-z/H)^2$ is the normalised eddy viscosity, $z=\hat{z}\hat{L}^{-1}$, $f = \hat{b} \hat{B}^{-1} + (i\sqrt{Pr})\hat{u}\hat{U}^{-1}$, $H=\hat{H}\hat{L}^{-1}$ and $z_0=\hat{z_0}\hat{L}^{-1}$, with boundary conditions $f(z_0)=-1$, $f(H) = 0$.
+%A similar linear transformation was used in \citet{Nieuwstadt1983}, to solve for the Ekman equations.
+%
+The canonical form of Eq. \ref{ode_norm} reads:
 %
 \begin{linenomath*}
-\begin{align}
+\begin{equation}
 	\label{can_form}
-	f''+P f'+ Qf &=0, && \mathrm{in}  \ [0,H^+]
-\end{align}
+	f_{zz}+P f_z+ Qf =0,
+\end{equation}
 \end{linenomath*}
 %
-where $P(z^+)=(K^+)'/K^+$ and $Q(z^+)=1/(\pm i K^+)$. Second, it is an easy computation to show that, if $f$ solves Eq. \ref{can_form} then $g(z^+):=f( (H^++2 \epsilon^+) z^+- \epsilon^+)$ solves:
+where $P(z)=K_{M,z} / K_M$ and $Q(z)= (-i \, \sqrt{Pr}) /K_M$. Second, it is straightforward to show that rewriting Eq. \ref{can_form} for $y= \frac{z }{H}
+$ results in
+%if $f$ solves Eq. \ref{can_form} then $g(z^+):=f( (H^++2 \epsilon^+) z^+- \epsilon^+)$ solves:
 %
 \begin{linenomath*}
-\begin{align}
+\begin{equation}
 	\label{can_form_sec}
-	g''+\widetilde{P} g'+ \widetilde{Q} g =0, && \mathrm{in}  \ [0,1]
-\end{align}
+	f_{yy}+\widetilde{P} f_y+ \widetilde{Q} f =0,
+\end{equation}
 \end{linenomath*}
 %
-where $\widetilde{P}(z^+)=\gamma'(z^+)/\gamma(z^+)$ and $\widetilde{Q}(z^+)=1/(\pm i \cdot A^+ \cdot (H^++2\epsilon^+) \gamma(z^+))$, with $\gamma(z^+)=z^+(z^+-1)^2$.
-Eqn. \ref{can_form_sec} is a second order ODE with three regular singular points at $z^+ = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
-This special case is known as the \emph{equation of Papperitz} and its general solution is:
+where $\widetilde{P}(y)=\gamma_y(y)/\gamma(y)$ and $\widetilde{Q}(y) = (-i \sqrt{Pr} H)/\gamma(y)$, with $\gamma(y)=y(y-1)^2$.
+Eq. \ref{can_form_sec} is a second order ordinary differential equation with three regular singular points at $y = 0,1$ and $\infty$, as in \citet{Morse1954a}. 
+This specific equation is known as the \emph{equation of Papperitz} and its general solution is:
 %
-%\begin{widetext}
 \begin{linenomath*}
 \begin{equation}
-	g(z^+) = \alpha (1-z^+)^\mu \ _2F_1 (\mu, 1- \mu', 1+\mu-\mu', 1-z^+)
-	+\beta (1-z^+)^{\mu'} \ _2F_1 (\mu', 1- \mu, 1+\mu'-\mu, 1-z^+),
+	f(y) = \alpha (1-y)^\mu \ _2F_1 (\mu, 1- \mu^{\prime}, 1+\mu-\mu^{\prime}, 1-y)
+	+\beta (1-y)^{\mu^{\prime}} \ _2F_1 (\mu^{\prime}, 1- \mu, 1+\mu^{\prime}-\mu, 1-y) \, ,
 	\label{gen_sol_g}
@@
 \end{linenomath*}
-%\end{widetext}
 %
-where $\ _2F_1$ are \emph{Gaussian hypergeometric functions} and $\mu$, $\mu'$ are the solutions to the degree two equation
+where $\ _2F_1$ are \emph{Gaussian hypergeometric functions} 
+%and 
+%%
+%\begin{equation}
+%	\mu = -\frac{1}{2} + \frac{1}{2}\sqrt{1+4 i \sqrt{Pr} H} \,  , \qquad 
+%	\mu^{\prime} = -\frac{1}{2} - \frac{1}{2}\sqrt{1+4 i \sqrt{Pr} H} \, ,
+%\end{equation}
+%
+and $\mu$, $\mu'$ are the solutions to the quadratic equation
+
+\begin{linenomath*}
+\begin{equation*}
+	x^2+x- i H \sqrt{Pr}=0.
+\end{equation*}
+\end{linenomath*}
+
+%Note that the general solution to Eq. \ref{can_form_sec} is also often written using the \emph{Riemann symbol}:
+%%
+%\begin{linenomath*}
+%\begin{equation*}
+%\left \{
+%\begin{array}{cccc}
+%0 & 1 & \infty &  \\
+%\lambda & \mu & \nu & y\\
+%\lambda' & \mu' & \nu' & \\
+%\end{array}
+%\right \}
+%\end{equation*}
+%\end{linenomath*}
+%%
+%where, in this case, $\mu$ and $\mu'$ are as above, $\lambda=\lambda'=0$ and $\nu=0$, $\nu'=2$.
+%
+Upon back-substitution of the independent variable and specification of the integration constants $\alpha$ and $\beta$ (through the imposition of boundary conditions), the solution in terms of $u$ and $b$ is derived by separating the real and imaginary part of $f$
 %
 \begin{linenomath*}
-\begin{equation*}
-	x^2+x+1/(\pm i A^+(H^++2 \epsilon^+))=0,
-\end{equation*}
+\begin{equation}
+	u(z) = -\frac{\operatorname{Im}(f(z))}{\sqrt{Pr}}, \qquad b(z) = \operatorname{Re}(f(z)).
+	\label{u_b_solutions}
+\end{equation}
 \end{linenomath*}
 %
-depending on which of Eqs. \ref{can_form_sec} we are solving.
-Note that the general solution to Eq. \ref{can_form_sec} is also often written using the \emph{Riemann symbol}:
-%
-\begin{linenomath*}
-\begin{equation*}
-\left \{
-\begin{array}{cccc}
-0 & 1 & \infty &  \\
-\lambda & \mu & \nu & z^+\\
-\lambda' & \mu' & \nu' & \\
-\end{array}
-\right \}
-\end{equation*}
-\end{linenomath*}
-%
-where, in this case, $\mu$ and $\mu'$ are as above, $\lambda=\lambda'=0$ and $\nu=0$, $\nu'=2$.
-%
-To retrieve the general solution to Eq. \ref{can_form} it is sufficient to substitute $(z^++\epsilon^+)/(H^+ +2 \epsilon^+)$ in place of $z^+$ in Eq. \ref{gen_sol_g}.
-As the integration constants $\alpha$ and $\beta$ are specified through the imposition of boundary conditions, back-substituting $b^+ = (f_1+f_2)/2$ and $u^+ = -(f_1-f_2)/2i$ yields the solution in terms of $u^+$ and $b^+$.
 
-% ####################################################################
+As stated in the introduction, the proposed derivation closely resembles that in \citet{Nieuwstadt1983a}, where the Ekman-layer equations have been solved in closed form for the same eddy viscosity coefficient.
+Here, the solution is specified for the Prandtl model equations, and generalised to account for arbitrary (constant) $Pr$.
+In addition, the proposed solution considers a finite $z_0$, as opposite to that in \citet{Nieuwstadt1983a} where the simplifying assumption $z_0=0$ was adopted.
+A finite $z_0$ (hence finite $K_M(z_0)$ and $K_H(z_0)$) is required when solving the Prandtl slope flow model, which would otherwise yield unphysical velocity and buoyancy profiles.
+%This behavior is in contrast to that of the Ekman-layer equations, and apparently related to the different forcing mechanism characterising the two systems.
+The formulation of $K_M(z)$ and $K_H(z)$ allows for exact integration of Eqs.
+\ref{Prandtl_eq}, hence providing a reference to study the dependence of the flow on the dimensionless model parameters $Pr$ and $z_0 \equiv \hat{z}_0 \hat{u}_* \kappa (\hat{N} \sin{\alpha})^{-1}$.
+It also represents a useful reference for the validation of numerical and patched/matched solutions.
+
+%Note that in general it is not possible to satisfy Eq. \ref{MOST1} directly, since the specification of $\hat{K}$ has to be done a-priori, and $\hat{u}_*$ depends on the solution. 
+%The chosen normalisation overcomes this limitation, and highlights the linear dependence of the length scales of the flow on $\hat{u}_*$ ($\hat{L} \propto \hat{u}_*)$.
+%One could therefore first solve for $u$ and $b$, compute $\hat{u}_* = (u_* \hat{b}_s/\hat{N})$, where $u_*=\kappa [z(du/dz)]_{z_0}$ is readily available from the normalised solution, and then re-dimentionalize the problem, imposing $\hat{A}=\kappa \hat{u}_* / \hat{\zeta}^2$, resulting in $\hat{K}(\hat{z})=\kappa \hat{u}_* \hat{z}$ in the near wall regions, in agreement with Eq.
+\ref{MOST1}.
+
 \section{Examples}
-%
+
+% GENERAL DESCRIPTION OF MAIN FEATURES 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}
    \begin{center}
-      \includegraphics[width= 70.0mm]{./u-b_log}
-      \caption{Comparison of the new analytic solution (A1) against the constant-$K$ (A2), the WKB (A3) and a numerical $1D$ solution (N1).
-Analytic profiles of normalized velocity $(u^+)$ are denoted with dot-dashed lines whereas analytic profiles of normalized buoyancy $(b^+)$ are denoted by dashed lines.
-Here $K^+ = A^+ \cdot (z^++\epsilon^+)(z^+-H^+-\epsilon^+)^2$ where $A^+=6.75 e-4$, $\epsilon^+ =1.5 \times 10^{-3}$ and $H^+ = 10$.
-A corresponding dimensional profile is characterized by $\max{(K)} = 0.1 \ \mathrm{m^2s^{-1}}$ and $K(z=0) = 10^{-5} \ \mathrm{m^2s^{-1}}$, in agreement with common atmospheric values.}
+      \includegraphics[width= 70.0mm]{comparison_analytic_solutions.eps}
+      \caption{Comparison of the proposed analytic solution (A1) against the constant-$K$ (A2) and the WKB solution (A3).
+$u$ is positive in the down-slope direction.
+The dashed black line identifies the adopted eddy viscosity $K_M$.
+The constant-$K$ value is fixed to $K_M^{\mathrm{A2}} = \max(K_M^{\mathrm{A1}})/3$.
+Velocity profiles $(u)$ are denoted with solid lines whereas buoyancy profiles $(b)$ are denoted by dashed lines.
+Here $z_0 = 0.001, \, Pr=1$ and $H = 12$.
+Assuming $\hat{N}=10^{-2} \ \mathrm{(Hz)}$, $\hat{\alpha}=5^{\circ}$ and $\hat{b}_s = -0.1 \ \mathrm{(m \, s^{-2})}$, the corresponding dimensional system, based on $u_* \equiv \hat{u}_* U^{-1}$ from the A1 solution, is characterized by $\hat{z}_0 = 0.08 \ \mathrm{(m)}$ and $\hat{u}_* = 0.18 \ \mathrm{(m \, s^{-1})}$, within the range of commonly observed atmospheric values.
+      A1 is indistinguishable to a corresponding second-order centered finite-difference numerical solution (also exact in double precision arithmetics), therefore the comparison is omitted.}
       \label{fig1}
@@
 %
+In Fig. \ref{fig1} we compare the proposed analytic solution (A1) against the constant-$K$ (A2) and the WKB solution (A3), considering $Pr=1$ (i.e., $\hat{K}_M = \hat{K}_H$).
+The constant-$K$ solution is evaluated based on Eqs. \ref{Prandtl_sol}, and the WKB solution is evaluated based on Eqs. \ref{WKB_sol}. 
+For the sake of comparison, A1 and A3 are evaluated for the same $z_0$ and $H$ (hence same $K(z)$) parameters, whereas A2 is computed imposing $K_{A2} = \max{(K)}/3$.
+$\hat{h}$ is evaluated iteratively in order to match $z_r$ of the A1 solution.
+Given that the resulting A1 solution is relatively insensitive to the exact $\hat{h}$ (in the neighborhood of the $\hat{h}=\hat{z}_r$ value) only a few iterations are necessary to provide a good approximation of the desired $\hat{K}$.
+The chosen $K(z)$ satisfies the constraints defined in \citet{Grisogono2002} for the validity of the WKB method.
+A1 shows a remarkably strong inversion in the near surface regions, when compared against its analytical counterparts, suggesting an over-diffusive behavior of both A2 and A3. 
+For instance, normalised surface buoyancy gradients of simulation A1 are over an order of magnitude larger than those of A3 ($b_z^{\mathrm{A1}}/b_z^{\mathrm{A3}} = \mathcal{O}(10)$ for $z \rightarrow z_0$).
+Nevertheless, $u_z^{\mathrm{A1}} \approx u_z^{\mathrm{A3}}$ for $z \rightarrow z_0$, confirming the better dissipative properties of A3, when compared against the constant-$K$ approach. 
+To underline the importance of a decreasing magnitude of eddy diffusivities as the surface is approached, it is worth noting that $u_z^{\mathrm{A1}}/ u_z^{\mathrm{A2}} = \mathcal{O}(10)$.
+Overall, the proposed normalised solution differs significantly when compared against A2 and A3, in both amplitude and location of extrema.
+Both the height of the LLJ and the peak velocity are significantly reduced, features that are of great importance for an accurate representation of the stable boundary layer and from a parameterisation perspective \citep{Mahrt1998}.
+Besides, A1 predicts significantly reduced mass and buoyancy (slope-parallel) fluxes, viz. $\int_0^{H}{u}{\, \mathrm{d}z}$ and $\int_0^{H}{b}{ \, \mathrm{d}z}$, with respect to A2 and A3.
+
+% Z0 DEPENDENCY 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}
     \begin{center}
-    \includegraphics[width= 70.0mm]{./u-b_log_various_K}
-    \caption{Sensitivity of A1 (left) and A3 (right) profiles to variations in the diffusivity coefficient $K^+$.
-Normalized velocity values $(u^+)$ are denoted with dot-dashed lines whereas normalized buoyancy values $(b^+)$ with dashed lines.
-Equations are integrated in  the interval $z^+ \in [0,10]$, which is fully shown in the plot.
-Here we considered $A^+=6.75 \times 10^{-4}$ and $\epsilon^+  = (7.4,1.5,0.30,0.06) \times 10^{-3}$.
-Under the constraint $K(z=0) = 10^{-5} \ \mathrm{m^2s^{-1}}$, the corresponding set of dimensional kynematic diffusivities satisfy $\max{(K)}=0.002,0.01,0.05,0.25 \ \mathrm{m^2s^{-1}}$.}
+    \begin{tabular}{c c}
+    	\includegraphics[width= 48.0mm]{z0_sensitivity_plot.eps} &
+	\includegraphics[width= 48.0mm]{z0_sensitivity_plot_grisogono.eps}
+    \end{tabular}
+    \caption{Sensitivity of the normalised A1 (left) and A3 (right) solutions to the $z_0$ parameter.
+Solid lines denote down-slope velocity $(u)$ whereas dashed lines denote buoyancy $(b)$.
+Fixed parameters: $H=12$, $Pr=1$.}
+    %Assuming $N=10^{-2} \ \mathrm{(Hz)}$, $\alpha=30 \ \mathrm{(deg)}$ and $b_s = -0.1 \ \mathrm{(ms^{-2})}$, the resulting dimensional profiles are characterised by $z_{0,1} = 0.0008 \ \mathrm{(m)}, u_{*,1} = 0.09 \ \mathrm{(ms^{-1})}$, $z_{0,2} = 0.01 \ \mathrm{(m)}, u_{*,2} = 0.18 \ \mathrm{(ms^{-1})}$ and $z_{0,3} = 0.3 \ \mathrm{(m)}, u_{*,3} = 0.39 \ \mathrm{(ms^{-1})}$ respectively.
+A lower portion of the domain is shown for both normalised and dimensional profiles.%
     \label{fig3}
@@
 %
-In Fig. \ref{fig1} we compare the new analytic solution (A1 in the following) against the constant-$K$ (A2), the WKB (A3) and a numerical solution (N1).
-The constant-$K$ value is fixed to $K^+_{\mathrm{A2}} = \max(K_{\mathrm{A1}}^+)/3$. 
-Profiles for N1 are derived by solving monolithically the system of ODEs defined by Eqs.
-\ref{eqn1u_norm} and \ref{eqn1b_norm}, adopting a second-order accurate centered finite difference discretization with over $40,000$ collocation points and stretching the grid via a quadratic coordinate transform (at such resolution profiles are invariant to further refinements down to machine precision).
-The excellent match between A1 and N1 certifies the quality of results for both methods. 
-In comparison to its analytical counterparts, A1 shows a remarkably strong inversion in the near surface regions $(z^+ <1)$, suggesting overdiffusive behaviour of both A2 and A3, which are incapable of providing such strong buoyancy gradients.
-For instance, normalized surface buoyancy gradients of simulation A1 are over an order of magnitude larger than those of A2 $( (db/dz)^+_\mathrm{A1}/(db/dz)^+_\mathrm{A2} = \mathcal{O}(10)$ as $z^+ \rightarrow 0$).
-Despite this, we observe a relatively good match between $u^+_\mathrm{A1}$ and $u^+_\mathrm{A3}$ in the interval $z^+ \in [0,1]$, which confirms the enhanced dissipative properties of the A3 solution, when compared against the constant-$K$ approach.
-To understand the importance of a decreasing eddy viscosity in the near surface regions, it is worth noting that $(du/dz)^+_\mathrm{A1}/(du/dz)^+_\mathrm{A2} = \mathcal{O}(10)$, whereas $(du/dz)^+_\mathrm{A1}/(du/dz)^+_\mathrm{A3}= \mathcal{O}(1)$ as $z^+ \rightarrow 0$.
-Overall the new solution exhibits significant variations when compared against A2 and A3, in both amplitude and location of maxima-minima. 
-For instance, both the low-level jet height and the peak normalized velocity are significantly reduced, features that are of great importance for an accurate representation of the stable boundary layer and from a parameterization perspective \citep{Mahrt1998}.
-Further, from Fig.
-\ref{fig3}, it is clear that $\max{(u^+_\mathrm{A1})}$ now depends on the diffusive properties of the flow, i.e.
-$\max{(u^+_{\mathrm{A1}})} = f(K^+)$, in constrast to its analytic counterparts, which predict $\max{(u^+_\mathrm{A2})} = \max{(u^+_\mathrm{A3})} =  \sqrt{2}/2 [(e^{(\pi/4)})/\sqrt{Pr}] = 0.32$, regardless of $K^+$.
-$u^+_{\mathrm{A1}}$ and $b^+_{\mathrm{A1}}$ also show a stronger dependence on the $K+$ parameter with respect to A3 profiles, in particular in the $z^+ \in [0,1]$ interval.
-Overall, A1 predicts significantly reduced mass and buoyancy (horizontal) fluxes, viz. $\int_0^{H^+}{u^+}{dz^+},\int_0^{H^+}{b^+}{dz^+}$, with respect to A3.
+%\begin{figure}
+%    \begin{center}
+%    \begin{tabular}{c c}
+%    	\includegraphics[width= 48.0mm]{./z0_sensitivity_plot_normalised_grisogono} &
+%	\includegraphics[width= 48.0mm]{./z0_sensitivity_plot_grisogono}
+%    \end{tabular}
+%    \caption{Sensitivity of the normalised A3 solution $(\overline{u},\overline{b})$ to the $\overline{z}_0$ parameter (left) and a corresponding family of dimensional profiles $(u,b)$ (right).
+Solid lines denote velocity profiles whereas dashed lines denote buoyancy profiles.
+Choice of model parameters: $\overline{\zeta}^{(i)}=10$, $\overline{z}_{0,1} = 0.0001$, $\overline{z}_{0,2} = 0.001$ and $\overline{z}_{0,3} = 0.01$.
+To re-dimensionalize the solution we assumed $N=10^{-2} \ \mathrm{(Hz)}$, $\alpha=30 \ \mathrm{(deg)}$ and $b_s = -0.1 \ \mathrm{(ms^{-2})}$.
+The resulting dimensional profiles are characterised by $z_{0,1} = 0.0002 \ \mathrm{(m)}, u_{*,1} = 0.024 \ \mathrm{(ms^{-1})}$, $z_{0,2} = 0.007 \ \mathrm{(m)}, u_{*,2} = 0.089 \ \mathrm{(ms^{-1})}$ and $z_{0,3} = 0.23 \ \mathrm{(m)}, u_{*,3} = 0.29 \ \mathrm{(ms^{-1})}$ respectively.
+A lower portion of the domain is shown for both normalised and dimensional profiles.}
+%    \label{fig4}
+%    \end{center}
+%\end{figure}
 %
-% new part
+The sensitivity of the solution to variations in the $z_0$ parameter is displayed in Fig. \ref{fig3}.
+Since $(u_*,b_*) \propto z_0$, where $b_* \equiv \kappa z b_z$, larger hydrodynamic roughness lengths $(z_0)$ correspond to stronger transfer rates of momentum and buoyancy in the vertical direction, yielding a larger $z_j$ and $\max{(u)}$.
+To highlight differences with respect to the WKB solution, the same $z_0$ sensitivity test is displayed for the A3 solution in Fig. \ref{fig3}.
+Because $K \approx z$ in the neighborhood of $z=z_0$, A3 predicts $z_j \approx \pi^2/32+z_0$ and $\max{(u)} = 0.32$.  
+A3 is therefore able to describe the $z_0$ (alias $K$) dependency of $z_j$, but predicts a $K$-invariant $\max{(u)}$, as is clear from Fig. \ref{fig3}.
+A2 is also characterized by a $K$-invariant $\max{(u)}$.
+The proposed solution therefore provides additional insight on the physics of the system, valid within the underlying Monin-Obukhov framework and idealized boundary conditions, suggesting a somewhat different coupling between the velocity and buoyancy fields, when compared to that predicted by previous analytic solutions of the linear Prandtl model.
+It shows that a larger $z_0$ parameter results in a higher and stronger LLJ ($[z_j,\max{(u)}] \propto z_0$).
+Further, since $\hat{L} = \kappa \hat{u}_*/(\hat{N} \sin{\alpha})$, the characteristic scale of the flow $(\hat{L})$ will vary proportionally to $z_0$ for a prescribed $\hat{U},\hat{B},\alpha$ set.
+
+%Further, given that A1 predics a larger $u_*$, when compared against A2 and A3, the re-dimensionalized solution is characterised by a larger characteristic scale L, as apparent if one compares the dimensional profiles in Fig.
+\ref{fig3} and \ref{fig4}.
+
+%Of practical interest from a parameterisation perspective is the relation between the internal and given external parameters of the problem $(u_*,b_*$ and $b_s,N,\alpha,z_0$ respectively).
+%From the normalised solution it is possible to compute:
+%%
+%\begin{eqnarray}
+%	\overline{u}_* = \kappa \overline{z}_0 \frac{d \overline{u}}{d\overline{z}}\bigg|_{\overline{z}_0} = f_1(\overline{z}_0) , \hspace{0.5cm}
+%	\overline{b}_* = \kappa \overline{z}_0 \frac{d \overline{b}}{d\overline{z}}\bigg|_{\overline{z}_0} = f_2(\overline{z}_0),
+%	\label{internal_external_parameters}
+%\end{eqnarray}
+%%
+%where $f_1,f_2$ are universal function of the dimensionless model parameters.
+%$f_1$ and $f_2$ are depicted in Figure \ref{fig7}.
+%$\overline{z}_0$ is chosen to encompass a vast range of realistic values of the dimensional hydrodynamic roughness length.
+%Given the computational burden of evaluating hypergeometric functions, we here provide a valid approximation of $f_1,f_2$, in the form of a power-law, expanded around the solution at $\overline{z}_0=10^{-5}$:
+%%
+%\begin{eqnarray}
+%	\overline{u}_* & = & 0.055 + 0.28 (\overline{z}_0-10^{-5})^{0.46}, \nonumber \\ 
+%	\overline{b}_* & = & 0.035 + 0.29 (\overline{z}_0-10^{-5})^{0.33}.
+%	\label{f1-f2}
+%\end{eqnarray}
+%%
+%Eqs. \ref{f1-f2}, together with the specified $b_s$ and $N$, allow to compute $u_* = \overline{u}_* \cdot b_s/N$ and $b_* = \overline{b}_*\cdot b_s$.
+%
+%\begin{figure}
+%   \begin{center}
+%      \includegraphics[width= 70.0mm]{./u-b_star_z0}
+%      \caption{Dependence of the non-dimensional internal parameters $\overline{u}_*, \overline{b}_*$ on $\overline{z}_0$.
+We here defined $\overline{u}_* = \kappa \overline{z}_0 (d \overline{u}/d\overline{z})|_{\overline{z}_0}$ and $\overline{b}_* = \kappa \overline{z}_0 (d \overline{b} / d\overline{z})|_{\overline{z}_0}$.
+Results are obtained for $\overline{\zeta}=10$.}
+%      \label{fig5}
+%   \end{center}
+%\end{figure}
+%
+
+%For completeness, we also provide simple formula for the computation of $\overline{z}_j$, $\overline{z}_r$, and $\max{(\overline{u})}$, which are of interest for dispersion studies in complex terrains:
+%%
+%\begin{eqnarray}
+%	\overline{z}_j & = & 0.051 + 1.48 (\overline{z}_0-10^{-5})^{0.48}, \nonumber \\ 
+%	\overline{z}_r & = & 4.552 + 2.34 (\overline{z}_0-10^{-5})^{0.36}, \\
+%	\max{(\overline{u})} & = & 0.107 + 0.23 (\overline{z}_0-10^{-5})^{0.22}. \nonumber
+%	\label{f3-f5}
+%\end{eqnarray}
+%
+%Eqs. \ref{f3-f5} are displayed in Fig. \ref{fig6}.
+%
+%\begin{figure}
+%   \begin{center}
+%      \includegraphics[width= 70.0mm]{./zj-zr_z0}
+%      \caption{Dependence of $\overline{z}_j$, $\overline{z}_r$, and $\max{(\overline{u})}$ on $\overline{z}_0$. Results are obtained for $\overline{\zeta}=10$.}
+%      \label{fig6}
+%   \end{center}
+%\end{figure} 
+%
+
+\begin{figure}
+    \begin{center}
+    \begin{tabular}{c c}
+    	\includegraphics[width= 48.0mm]{Pr_sensitivity_plot.eps} &
+	\includegraphics[width= 48.0mm]{Pr_sensitivity_plot_grisogono.eps}
+    \end{tabular}
+    \caption{Sensitivity of the normalised A1 (left) and A3 (right) solutions to the $Pr$ parameter.
+Solid lines denote down-slope velocity $(u)$ and dashed lines denote buoyancy $(b)$.
+Displayed solutions correspond to: $H=12$, $z_0 = 0.001$.}
+    \label{fig4}
+    \end{center}
+\end{figure}
+%
+Under stably stratified environments, pressure fluctuations induced by breaking gravity waves sum to those induced by turbulence, and yield an increase in the total momentum flux, without directly influencing the buoyancy flux \citep{Mahrt1998}.
+This results in turbulent Prandtl numbers that are usually greater than unity.
+Variations by a factor of 2 for $Pr$, perhaps even more under conditions of strong stratification, are common and that can lead to considerable changes in the shapes of vertical profiles of velocity and buoyancy.
+The sensitivity of the solution to variations in the $Pr$ parameter is displayed in Fig. \ref{fig4}. As before in Fig. \ref{fig3}, the closed form solution (A1) is compared to the WKB solution (A3).
+Variations in $Pr$ change the solution throughout the domain for both A1 and A3, larger $Pr$ results in weaker thermal and dynamic boundary-layers, and in a proportional decrease in $u_j$ and $z_j$. 
+Such a behavior could have been anticipated, since a larger $Pr$ in conjunction with the constant (imposed) surface buoyancy is expected to result in a lower surface buoyancy flux, i.e.
+in a lower rate of potential energy injected into the system.
+
+To study the sensitivity of the solution on the $h$ parameter we considered a $\pm 10 \%$ $h$-variation, and results are displayed in Fig. \ref{fig5}.
+Despite the non-negligible changes in $K(z)$ in the outer regions of the flow we observe a modest $\approx \pm 0.5 \%$ variation in $\max{(u)}$ and a $\approx \pm 5 \%$ variation in $z_j$, $\min{(u)}$ and $z_r$ (the location of $\min{(u)}$), which is well within the degree of accuracy of the current study.
+Recall that variations in $h$ lead to the same first order Taylor expansion of $K(z)$ around $z_0$, therefore the inner regions of the flow are relatively insensitive to the exact $h$ value.
+
+% PRACTICAL NOTES 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{On the computation of the solution}
+
 %
@@
     \begin{center}
-    \includegraphics[width= 70.0mm]{./u_dim_alpha_N_b}
-    \caption{Family of dimensional velocity profiles derived from re-dimensionalization of a reference normalized solution.
-The normalized solution is obtained in $z^+ \in [0,10]$ for $A^+ = 6.75 \times 10^{-4}$ and $\epsilon^+ =1.5 \times 10^{-3}$ (assuming $K(z=0) = 10^{-5}  \ \mathrm{m^2s^{-1}}$, the corresponding dimensional kynematic diffusivities satisfy $\max{(K)}=0.01 \ \mathrm{m^2s^{-1}}$).
-The considered set of parameters are reported in Table \ref{table}.
-Decreasing values of the parameters (with respect to the reference ones) are denoted with solid lines, increasing values by dashed lines.}
-    \label{fig2}
+    \begin{tabular}{c c}
+	\includegraphics[width= 48.0mm]{H_sensitivity_plot.eps} &
+	\includegraphics[width= 48.0mm]{halfwidth_convergence_zj_um.eps}
+   \end{tabular}
+    \caption{Left plot: Sensitivity of velocity $u$ (solid lines) and buoyancy $b$ (dashed lines) profiles on the $H$ parameter for the A1 solution.
+Right plot: convergence test, relative percentage error for $z_j$ (red lines) and $\max{(u)}$ (blue lines) as a function of $N$, where $N$ represents the number of terms considered in the truncated $_2F_1$ series.
+Parameters for the $H$-sensitivity study (left plot): $H_1=11.2$, $H_2=14$, $H_3=16.8$ and $z_0=0.001$.
+Parameters for the convergence test (right plot): $z_0 = 0.00001$ (squares), $z_0 = 0.0001$ (circles), $z_0 = 0.001$ (crosses) and $H=14$.
+We define $e_{z_j} = 100(z^N_j-z_j)/z_j$ and $e_{\max{(u)}} = 100[\max{(u^N)}-\max{(u)}]/\max{(u)}$, where $(\cdot)^N$ represents a quantity computed truncating the $_2F_1$ series to $N$ terms, and where $z_j$ and $\max{(u)}$ represent quantities that are exact in double precision arithmetic.
+}
+    \label{fig5}
     \end{center}
@@
 %
-\begin{table}
-\caption{Set of parameters for re-normalization of the reference solution.
-The reference normalized solution is computed adopting $H^+ = 10, A^+ = 6.75 \times 10^{-4}, \epsilon^+ =1.5 \times 10^{-3}$.}
-\label{table}
-\centering
-\begin{tabular}{l l l l l l l l}
-\hline
- Value & Ref. & $\alpha1$ & $\alpha_2$ & $N_1$ & $N_2$ & $b_{s,1}$ & $b_{s,2}$ \\
-\hline
-   $\alpha \ (\mathrm{deg})$ & 30 & 15 & 60 & 30 & 30 & 30 & 30  \\
-   $N \ (\mathrm{Hz})$ & 0.01 & 0.01 & 0.01 & 0.005 & 0.02 & 0.01 & 0.01 \\
-   $b_s \ (\mathrm{ms^{-2}})$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 & 0.15 & 0.60 \\
-\hline
-\end{tabular}
-\end{table}
-%
-To get acquainted with the proposed normalization Fig. \ref{fig2} proposes a set of re-dimensionalized velocity profiles $u \ \mathrm{(ms^{-1})}$ from a reference normalized solution.
-We propose a reference dimensional solution, characterized by $\alpha = 30 \ \mathrm{deg}, N = 0.01 \ \mathrm{Hz}$ and $b_s = 0.3  \ \mathrm{ms^{-2}}$, and consider variations in both sloping angle $\alpha$, imposed buoyancy frequency $N$ and imposed surface buoyancy $b_s$ (see Table \ref{table}).
-Variations in the sloping angle $\alpha$ result in a modification of the normalization constant $L \propto \sin^{-1/2}$ which acts as a stretching of the independent variable $z$ (no effects on $\max{(u)}$).
-In particular, the steeper the angle, the smaller the characteristic scales of the flow will become.
-Variations in the background stratification, viz.
+The computation of the Gauss hypergeometric function $_2F_1$ with all its parameters complex is known to be a non-trivial task.
+Although the $_2F_1$ function is merely a power series expansion (whose implementation is immediate), its use is prone to cancellation and round-off error, which become especially significant for certain ranges of the parameters and of the independent variable \citep{temme2007}.
+In our case, the solution $f = b+iu$ is evaluated in $y \in (z_0 / H, 1)$, which is within the radius of convergence $(R)$ of the hypergeometric functions that define $f$ (the radius of convergence of $_2F_1(a,b,c,y)$ is $|y|=1$).
+The solution computed here represents the $_2F_1$ functions as truncated power series, i.e.
+$_2F_1(a,b,c,y) = [(a)_k(b)_k]/[(c)_k k!] y^k$, where $a,b,c$ are the three input parameters, $(\cdot)_k$ is the Pochhammer symbol and $k!$ denotes the factorial of $k=1,2,\dots N$.
+All computations are performed in double precision arithmetic.
+In Fig. \ref{fig5} we display the convergence of the solution, in terms of $z_j$ and $\max{(u)}$, for a given set of $z_0$ values and $H =10$. 
+The solution shows sub-logarithmic convergence for both $e_{z_j} = 100(z^N_j-z_j)/z_j$ and $e_{\max{(u)}} = 100[\max{(u^N)}-\max{(u)}]/\max{(u)}$, and clearly, the smaller the $z_0$ parameter, the slower the resulting convergence rate.
+This behavior is justified by the fact that as $z_0$ is reduced, the solution is evaluated closer to $R$, where the convergence of $_2F_1$ in its power series form is known to be retarded.
+Despite the slow convergence of the series summation, the evaluation of the solution is stable throughout the range of realistic $z_0$.
+Note that the efficacy of the series summation could be much improved by various techniques (e.g., Shanks method, Pad\'e summation, etc.), but such an analysis is beyond the goal of the current study.
+
+%\begin{table}
+%\caption{Set of parameters for re-normalisation of the reference solution.
+The reference normalised solution is computed adopting $H^+ = 10, A^+ = 6.75 \times 10^{-4}, \epsilon^+ =1.5 \times 10^{-3}$.}
+%\label{table}
+%\centering
+%\begin{tabular}{l l l l l l l l}
+%\hline
+% Value & Ref. & $\alpha1$ & $\alpha_2$ & $N_1$ & $N_2$ & $b_{s,1}$ & $b_{s,2}$ \\
+%\hline
+%   $\alpha \ (\mathrm{deg})$ & 30 & 15 & 60 & 30 & 30 & 30 & 30  \\
+%   $N \ (\mathrm{Hz})$ & 0.01 & 0.01 & 0.01 & 0.005 & 0.02 & 0.01 & 0.01 \\
+%   $b_s \ (\mathrm{ms^{-2}})$ & 0.30 & 0.30 & 0.30 & 0.30 & 0.30 & 0.15 & 0.60 \\
+%\hline
+%\end{tabular}
+%\end{table}
+
+%To get acquainted with the proposed normalisation Fig. \ref{fig2} proposes a set of re-dimensionalized velocity profiles $u \ \mathrm{(ms^{-1})}$ from a reference normalised solution.
+%We propose a reference dimensional solution, characterised by $\alpha = 30 \ \mathrm{(deg)}, N = 0.01 \ \mathrm{(Hz)}$ and $b_s = -0.1  \ \mathrm{(ms^{-2})}$, and consider variations in both sloping angle $\alpha$, imposed buoyancy frequency $N$ and imposed surface buoyancy $b_s$ (see Table \ref{table}).
+%Variations in the sloping angle $\alpha$ result in a modification of the normalisation constant $L \propto \sin^{-1/2}$ which acts as a stretching of the independent variable $z$ (no effects on $\max{(u)}$).
+%In particular, the steeper the angle, the smaller the characteristic scales of the flow will become.
+%Variations in the background stratification, viz.
 $N$, will modify both $L \propto N^{-1/2}$ and $U \propto N^{-1}$, yielding changes in the system, whose lengths and velocities will tend to decrease (increase) with increasing (decreasing) $N$.
-Further, variations in the prescribed surface buoyancy $b_s$ will scale both buoyancy and velocity profiles accordingly, since $b(z) \propto b_s$ and $u(z) \propto b_s$.
-As in both the classic Prandtl and WKB linear models, $K^+$ needs to be assigned a-priori; it is not coupled and does not feed back into the solution, which represents the main weakness of such linear approaches \citep{grisogono2001katabatic}.
+%Further, variations in the prescribed surface buoyancy $b_s$ will scale both buoyancy and velocity profiles accordingly, since $b(z) \propto b_s$ and $u(z) \propto b_s$.
 
@@
 %
-We have derived a closed-form analytic solution of the Prandtl model equations, based on an ad hoc decoupling of the system and specific choice of the model parameter, resulting in a set of \textit{equations of Papperitz}, characterized by three regular singular points.
-The new solution is valid for O'Brien-type eddy diffusivities (cubic polynomials) and Prandtl number of unity. 
-For the considered settings the new solution represents an improvement with respect to both the classic constant-$K$ and the more recent WKB solutions. 
-New profiles show significant variations in both phase and amplitude of minima-maxima, stronger surface gradients are combined with overall reduced horizontal fluxes and the LLJ is further displaced toward the wall.
-The new solution suggests a somewhat different coupling between velocity and buoyancy -- when compared against its analytical counterparts, showing a diffusivity dependent peak velocity and a remarkably strong inversion layer in the near surface location.
-In addition to a theoretical insight, the proposed solution can be used to improve future stable boundary layer parameterizations when coupled with other parts of the boundary layer physics.
+A closed form solution of the Prandtl model equations has been proposed herein, valid for O'Brien-type eddy diffusivities and constant Prandtl number. 
+The solution is for katabatic flows and is an adaptation of the solution proposed in \citet{Nieuwstadt1983a} for the Ekman-layer equations, generalized to account for constant $Pr \neq 1$.
+Its characteristics have been discussed assuming transfer coefficients for momentum and buoyancy in accordance to Monin-Obukhov similarity (albeit the solution lend itself to more general $K$-parameterisations).
+The dependence of the normalised solution on the model dimensionless parameters $Pr$ and $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$ has been tested and compared against corresponding WKB solutions. 
+For the same geometrical and physical parameters, profiles show significant variations in both phase and amplitude of extrema with respect to their WKB counterparts: stronger surface gradients (inversely proportional to $Pr$) are combined with overall reduced slope-parallel fluxes, and the LLJ is further displaced toward the wall.
+In addition, its peak velocity, LLJ height, and surface gradients proved to be highly sensitive to variations of the dimensionless parameter $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$, highlighting a more complex coupling between the velocity and buoyancy fields.
+Despite the slow convergence of the series summation, which can however be accelerated through various techniques, the evaluation of the solution is stable throughout the range of realistic $z_0$.
+The proposed model can be of use to validate numerical or patched / matched solutions of the Prandtl equations, and to improve future stable boundary layer parameterisations, when coupled with other parts of the boundary layer physics.
 
@@
 %
-This research was primarily funded by the Swiss National Science Foundation (SNSF-200021-134892) and by the Competence Center for Environmental Sustainability (CCES-SwissEx) of the ETH domain.
-We are also grateful for funding from the NSERC Discovery Grant program.
+This research was funded by the Swiss National Science Foundation (SNSF-200021-134892), the Competence Center for Environmental Sustainability (CCES-SwissEx) of the ETH domain, and the NSERC Discovery Grant program.
+We are grateful to the peer reviewers whose comments helped to improve the overall quality of the manuscript.
 
@@
 % BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spbasic_nourl}      % basic style, author-year citations
 %\bibliographystyle{spmpsci}      % mathematics and physical sciences
 %\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{/Users/mg/Phd/papers/bib_files/library}
-
-\begin{thebibliography}{26}
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{{#1}}
-\providecommand{\urlprefix}{URL }
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-  \urlstyle{rm}\Url}\fi
-\providecommand{\eprint}[2][]{\url{#2}}
-
-\bibitem[{Chu(1987)}]{Chu1987}
-Chu PC (1987) {An instability theory of ice-air interaction for the formation
-  of ice edge bands}. Journal of Geophysical Research 92(7):6966,
-  \doi{10.1029/JC092iC07p06966}
-
-\bibitem[{Egger(1985)}]{Egger1985}
-Egger J (1985) {Slope Winds and the Axisymmetric Circulation over Antarctica}.
-  Journal of the Atmospheric Sciences 42:1859--1867,
-  \doi{10.1175/1520-0469(1985)042<1859:SWATAC>2.0.CO;2}
-
-\bibitem[{Fedorovich and Shapiro(2009{\natexlab{a}})}]{Fedorovich2009d}
-Fedorovich E, Shapiro A (2009{\natexlab{a}}) {Structure of numerically
-  simulated katabatic and anabatic flows along steep slopes}. Acta Geophysica
-  57(4):981--1010, \doi{10.2478/s11600-009-0027-4},
-  \urlprefix\url{http://www.springerlink.com/index/10.2478/s11600-009-0027-4}
-
-\bibitem[{Fedorovich and Shapiro(2009{\natexlab{b}})}]{Fedorovich2009}
-Fedorovich E, Shapiro A (2009{\natexlab{b}}) {Turbulent natural convection
-  along a vertical plate immersed in a stably stratified fluid}. Journal of
-  Fluid Mechanics 636:41, \doi{10.1017/S0022112009007757}
-
-\bibitem[{Grisogono and Oerlemans(2001)}]{grisogono2001katabatic}
-Grisogono B, Oerlemans J (2001) {Katabatic Flow: Analytic Solution for
-  Gradually Varying Eddy Diffusivities}. Journal of the Atmospheric Sciences
-  58(21):3349--3354,
-  \doi{http://dx.doi.org/10.1175/1520-0469(2001)058<3349:KFASFG>2.0.CO;2}
-
-\bibitem[{Grisogono and Oerlemans(2002)}]{Grisogono2002}
-Grisogono B, Oerlemans J (2002) {Justifying the WKB approximation in pure
-  katabatic flows}. Tellus, A 54(5):453--462,
-  \doi{10.1034/j.1600-0870.2002.201399.x}
-
-\bibitem[{Gutman(1983)}]{gutman_1983}
-Gutman LN (1983) {On the theory of the katabatic slope wind}. Tellus, A
-  35(3):332--335, \doi{10.3402/tellusa.v35i3.11434}
-
-\bibitem[{Gutman and Malbakhov(1964)}]{Gutman1964}
-Gutman LN, Malbakhov VM (1964) {On the Theory of the Katabatic Winds of
-  Antarctica}. University of Melbourne, Meteorology Department
-
-\bibitem[{Lykosov and Gutman(1972)}]{Lykosov_1972}
-Lykosov VN, Gutman LN (1972) {Turbulent boundary layer above a sloping
-  inderlying surface}. Proceedings of the USSR Academy of Sciences 8:799--809,
-  \urlprefix\url{papers2://publication/uuid/B2EC0692-4251-4224-8185-A1AE8D9B00E9}
-
-\bibitem[{Mahrt(1998)}]{Mahrt1998}
-Mahrt L (1998) {Stratified Atmospheric Boundary Layers and Breakdown of
-  Models}. In: Theoretical and Computational Fluid Dynamics, vol~11, pp
-  263--279, \doi{10.1007/s001620050093},
-  \urlprefix\url{http://link.springer.com/10.1007/s001620050093}
-
-\bibitem[{Monti et~al.(2002)Monti, Fernando, Princevac, Chan, Kowalewski, and
-  Pardyjak}]{Monti2002}
-Monti P, Fernando HJS, Princevac M, Chan WC, Kowalewski TA, Pardyjak ER (2002)
-  {Observations of Flow and Turbulence in the Nocturnal Boundary Layer over a
-  Slope}. Journal of the Atmospheric Sciences 59:2513--2534,
-  \doi{10.1175/1520-0469(2002)059<2513:OOFATI>2.0.CO;2}
-
-\bibitem[{Morse and Feshbach(1953)}]{Morse1954a}
-Morse PM, Feshbach H (1953) {Methods of Theoretical Physics}. McGraw-Hill
-
-\bibitem[{Nadeau et~al.(2013)Nadeau, Pardyjak, Higgins, and
-  Parlange}]{Nadeau2012}
-Nadeau DF, Pardyjak ER, Higgins CW, Parlange MB (2013) {Similarity Scaling Over
-  a Steep Alpine Slope}. Boundary-Layer Meteorology 147(3):401--419,
-  \doi{10.1007/s10546-012-9787-5},
-  \urlprefix\url{http://link.springer.com/10.1007/s10546-012-9787-5}
-
-\bibitem[{Nappo and Shankar(1987)}]{NAPPO1987}
-Nappo CJ, Shankar RK (1987) {A model study of pure katabatic flows}. Tellus A
-  39(1):61--71, \doi{10.3402/tellusa.v39i1.11740},
-  \urlprefix\url{http://onlinelibrary.wiley.com/doi/10.1111/j.1600-0870.1987.tb00289.x/abstract}
-
-\bibitem[{Nylen et~al.(2004)Nylen, {Andrew G. F.}, and Doran}]{Nylen2004b}
-Nylen TH, {Andrew G F}, Doran PT (2004) {Climatology of katabatic winds in the
-  McMurdo dry valleys, southern Victoria Land, Antarctica}. Journal of
-  Geophysical Research 109:1--9, \doi{10.1029/2003JD003937}
-
-\bibitem[{O'Brien(1970)}]{O'Brien1970}
-O'Brien JJ (1970) {A Note on the Vertical Structure of the Eddy Exchange
-  Coefficient in the Planetary Boundary Layer}. Journal of the Atmospheric
-  Sciences 27:1213--1215,
-  \doi{10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2},
-  \urlprefix\url{http://dx.doi.org/10.1175/1520-0469(1970)027<1213:ANOTVS>2.0.CO;2}
-
-\bibitem[{Oerlemans(1998)}]{Oerlemans1998}
-Oerlemans J (1998) {The atmospheric boundary layer over melting glaciers}. In:
-  Clear and Cloudy Boundary Layers, vol~48, Royal Netherlands Academy of Arts
-  and Sciences, pp 129--153,
-  \urlprefix\url{http://igitur-archive.library.uu.nl/phys/2007-0716-203217/oerlemans\_07\_atmosphericboundarylayer.pdf}
-
-\bibitem[{Oerlemans and Vugts(1993)}]{Oerlemans1993}
-Oerlemans J, Vugts HF (1993) {A Meteorological Experiment in the Melting Zone
-  of the Greenland Ice Sheet}. Bulletin of the American Meteorological Society
-  74(3):355--365, \doi{10.1175/1520-0477(1993)074<0355:AMEITM>2.0.CO;2}
-
-\bibitem[{Oldroyd et~al.(2014)Oldroyd, Katul, Pardyjak, and
-  Parlange}]{Oldroyd2014}
-Oldroyd HJ, Katul G, Pardyjak ER, Parlange MB (2014) {Momentum balance of
-  katabatic flow on steep slopes covered with short vegetation}. Geophysical
-  Research Letters 41:4761--4768, \doi{10.1002/2014GL060313}
-
-\bibitem[{Parish(1992)}]{Parish1992}
-Parish TR (1992) {On the Role of Antarctic Katabatic Winds in Forcing
-  Large-Scale Tropospheric Motions}. Journal of the Atmospheric Sciences
-  49:1374--1385, \doi{10.1175/1520-0469(1992)049<1374:OTROAK>2.0.CO;2}
-
-\bibitem[{Parish and Bromwich(1998)}]{Parish1998}
-Parish TR, Bromwich DH (1998) {A Case Study of Antarctic Katabatic Wind
-  Interaction with Large-Scale Forcing}. Monthly Weather Review 126:199--209,
-  \doi{10.1175/1520-0493(1998)126<0199:ACSOAK>2.0.CO;2}
-
-\bibitem[{Prandtl(1942)}]{Prandtl}
-Prandtl L (1942) {F\"{u}hrer durch die Str\"{o}mungslehre}. Vieweg \& Sohn,
-  Braunschweig
-
-\bibitem[{Shapiro and Fedorovich(2004{\natexlab{a}})}]{Shapiro2004a}
-Shapiro A, Fedorovich E (2004{\natexlab{a}}) {Prandtl number dependence of
-  unsteady natural convection along a vertical plate in a stably stratified
-  fluid}. International Journal of Heat and Mass Transfer 47(22):4911--4927,
-  \doi{10.1016/j.ijheatmasstransfer.2004.04.035},
-  \urlprefix\url{http://linkinghub.elsevier.com/retrieve/pii/S0017931004002157}
-
-\bibitem[{Shapiro and Fedorovich(2004{\natexlab{b}})}]{Shapiro2004}
-Shapiro A, Fedorovich E (2004{\natexlab{b}}) {Unsteady convectively driven flow
-  along a vertical plate immersed in a stably stratified fluid}. Journal of
-  Fluid Mechanics 498:333--352, \doi{10.1017/S0022112003006803},
-  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112003006803}
-
-\bibitem[{Shapiro and Fedorovich(2007)}]{Shapiro2007}
-Shapiro A, Fedorovich E (2007) {Katabatic flow along a differentially cooled
-  sloping surface}. Journal of Fluid Mechanics 571:149,
-  \doi{10.1017/S0022112006003302},
-  \urlprefix\url{http://www.journals.cambridge.org/abstract\_S0022112006003302}
-
-\bibitem[{Spalart et~al.(2011)Spalart, Strelets, and
-  Garbaruk}]{Burkholder2011a}
-Spalart P, Strelets M, Garbaruk A (2011) {Quality and Reliability of Large-Eddy
-  Simulations II}. In: Evaluating Subgrid-ScaleModels for Large-Eddy Simulation
-  of Turbulent Katabatic Flow, vol~16, pp 253--267,
-  \doi{10.1007/978-94-007-0231-8},
-  \urlprefix\url{http://www.springerlink.com/index/10.1007/978-94-007-0231-8}
-
-\end{thebibliography}
+\bibliography{/Users/mg/Phd/papers/bib_files/library}
 

### 2016-06-23 paper_BLM.tex
last review version

@@
 The characteristics of the solution are discussed as a function of the dimensionless model parameters $Pr$ and $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$, where $\hat{z}_0$ is the hydrodynamic roughness length, $\hat{b}_s$ is the imposed surface buoyancy and $\hat{N}$ is the Brunt-V\"ais\"al\"a frequency.
-For the considered range of such parameters, velocity and buoyancy profiles show significant variations in both phase and amplitude of extrema with respect to the classic constant-$K$ model and a more recent approximate solution based on the Wentzel-Kramers-Brillouin (WKB) theory.
+For the considered range of such parameters, velocity and buoyancy profiles show significant variations in both phase and amplitude of extrema with respect to the classic constant $K$ model and a more recent approximate solution based on the Wentzel-Kramers-Brillouin theory.
 Near-wall regions are characterized by relatively stronger surface momentum and buoyancy gradients, whose magnitude is inversely proportional to $Pr$.
-In addition, slope-parallel momentum and buoyancy fluxes are reduced, the low-level jet (LLJ) is further displaced toward the wall, and its peak velocity strongly depends on $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$.
+In addition, slope-parallel momentum and buoyancy fluxes are reduced, the low-level jet is further displaced toward the wall, and its peak velocity strongly depends on $\hat{z}_0 \hat{N}^2 \hat{b}_s^{-1}$.
 
@@
 Here, a closed-form solution to the Prandtl-model equations is derived on a finite domain ($\hat{z} \in [\hat{z}_0,\hat{H}]$), valid for eddy viscosity and diffusivity coefficients that are modeled as a limited range of cubic polynomials, similar to what was proposed in \citet{O'Brien1970} for the planetary boundary layer.
-The derivation is a generalization of the solution proposed in \citet{Nieuwstadt1983a}, where the Ekman-layer equations were solved for the same form of momentum transfer coefficient.
+The derivation is a generalization of the solution proposed in \citet{Nieuwstadt1983a}, where the Ekman-layer equations were solved for the same form of the eddy viscosity / diffusivity parameters, and $Pr=1$.
 Recall that the Ekman-layer equations can be reduced to the Prandtl equations after simple changes of variables \citep{Veronis1970}. 
